### 2021-09-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e8ea02af51b97f75bfd818b4c6dc6fa8ea7779fb 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences

\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

Requirements

\begin{quote}
Candidates must submit a thesis proposal at least 7 days prior to the
examination. It is the student's responsibility to provide each member
of the Examining Committee with a copy, as well as Ancil Gittens in the
graduate office. The thesis proposal should address the relevant
background, the specific questions to be asked and their significance,
the approach and methods, results already obtained, and the anticipated
schedule. The proposal should be no more than 10 double-spaced pages (12
font). This limit does not include tables, figures, figure legends,
bibliography or the planned timeline to complete work. Committee members
will not be responsible for reviewing text in excess of the page limit.
The written proposal may include preliminary results if available but
must address the whole scope (all chapters) of the projected thesis.\\
The proposal serves two purposes. First, it defines the research area
and thus forms a basis for questioning. Second, it is itself part of the
evidence upon which a final evaluation will be made. For these reasons,
it should be written with care. Please see the additional tips on
proposal writing in the document titled ``QE Expectations and Advice''
(weblink available on Biology Graduate Studies webpage
\end{quote}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\begin{quote}
The student must provide a written proposal for their project to their
QE examining committee at least 7 days prior to the scheduled QE. An
acceptable proposal must be provided at least 7 days in advance or the
QE may need to be rescheduled. It is strongly recommended that a draft
of the proposal be provided to the supervisory committee at least a few
days prior to the supervisory committee meeting mentioned above. This
allows for maximal feedback to be incorporated prior to the QE. The
proposal should be similar in nature to an NSERC grant application
describing the research approach. In general in your proposal and in all
future scientific writing, using subheadings and clear writing to help
the reader is a good idea. The guidelines mandate a proposal of 2500
words (approximately 10 pages double spaced). This limit does not
include tables, figures, bibliography, figure legends, or a planned
timeline to complete work. This 2500 word limit will be enforced. A
proposal of 12 pages might not be rejected (or it might), but a proposal
of 15 pages definitely will. Similarly, the presentation at the start of
the QE is required to be 1520 minutes. This will also be enforced. Both
the written proposal and the oral presentation may include preliminary
results if available but must address the whole of the projected thesis.
- A successful QE will depend heavily on a top-quality proposal. This
proposal should go through multiple drafts and be honed to a very finely
worded document that shows the clarity of your thinking through
conciseness and exact statements. Some topics you should probably cover
are listed below. We recommend discussing omissions from this list with
your advisor and your supervisory committee if you think some of these
sections are not relevant to your particular project. - Brief review of
the current state of knowledge - Precise statement of the question
and/or hypotheses - Description of the methods - Detailed description of
the experimental or sample design. Be clear about what factors are being
controlled or sampled. Provide specific numbers for how many levels of
each factor are planned, and how many replicates/samples within each
factor. Address any issues that arise from finite effort levels in terms
of tradeoffs between replication within vs.~between factors
(i.e.~describe why your plan is optimal). Provide a realistic estimate
of the amount of time this will require in the lab or field. -
Statistical analysis approach. Describe specific statistical approaches,
the output of these approaches, how these can be used to test your
hypotheses, assumptions of the tests, and potential problems. - If you
will be using novel measurement techniques, provide a detailed
description (if you are using standard techniques then references to the
standard techniques are enough). - Provide a description of each chapter
anticipated in the dissertation (this - may be incorporated into the
above sections or as a separate section). - A brief statement of the
broader importance of the question to your field and to society -
Provide a timeline showing when the research and writing will be
performed - (this can be an appendix that does not count against your
\end{quote}

\end{document}

### 2021-09-24 preprint.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e8ea02af51b97f75bfd818b4c6dc6fa8ea7779fb 🚀

--- 2021-09-24 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 \,\textsuperscript{1,2}
-
-\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences
-
+\vskip 1em
+\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences\\
+\vskip 1em
 \textbf{Correspondance to:}\\
 Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2021-09-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@87dc253f76ad2deac20ab4c72ec8ddec6a91188d 🚀

@@
 The written proposal may include preliminary results if available but
-must address the whole scope (all chapters) of the projected thesis.\\
-The proposal serves two purposes. First, it defines the research area
-and thus forms a basis for questioning. Second, it is itself part of the
+must address the whole scope (all chapters) of the projected thesis. The
+proposal serves two purposes. First, it defines the research area and
+thus forms a basis for questioning. Second, it is itself part of the
 evidence upon which a final evaluation will be made. For these reasons,
@@
 Provide a timeline showing when the research and writing will be
-performed - (this can be an appendix that does not count against your
+performed
 \end{quote}

### 2021-09-30 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@360fc338319d133f48334175d30238691dd10a46 🚀

@@
 
-Requirements
+Forecasting in ecology.
 
-\begin{quote}
-Candidates must submit a thesis proposal at least 7 days prior to the
-examination. It is the student's responsibility to provide each member
-of the Examining Committee with a copy, as well as Ancil Gittens in the
-graduate office. The thesis proposal should address the relevant
-background, the specific questions to be asked and their significance,
-the approach and methods, results already obtained, and the anticipated
-schedule. The proposal should be no more than 10 double-spaced pages (12
-font). This limit does not include tables, figures, figure legends,
-bibliography or the planned timeline to complete work. Committee members
-will not be responsible for reviewing text in excess of the page limit.
-The written proposal may include preliminary results if available but
-must address the whole scope (all chapters) of the projected thesis. The
-proposal serves two purposes. First, it defines the research area and
-thus forms a basis for questioning. Second, it is itself part of the
-evidence upon which a final evaluation will be made. For these reasons,
-it should be written with care. Please see the additional tips on
-proposal writing in the document titled ``QE Expectations and Advice''
-(weblink available on Biology Graduate Studies webpage
-\end{quote}
+Forecasting in weather, introduce computers.
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+Future is uncertain, how do we best act given a forecast?
 
-\begin{quote}
-The student must provide a written proposal for their project to their
-QE examining committee at least 7 days prior to the scheduled QE. An
-acceptable proposal must be provided at least 7 days in advance or the
-QE may need to be rescheduled. It is strongly recommended that a draft
-of the proposal be provided to the supervisory committee at least a few
-days prior to the supervisory committee meeting mentioned above. This
-allows for maximal feedback to be incorporated prior to the QE. The
-proposal should be similar in nature to an NSERC grant application
-describing the research approach. In general in your proposal and in all
-future scientific writing, using subheadings and clear writing to help
-the reader is a good idea. The guidelines mandate a proposal of 2500
-words (approximately 10 pages double spaced). This limit does not
-include tables, figures, bibliography, figure legends, or a planned
-timeline to complete work. This 2500 word limit will be enforced. A
-proposal of 12 pages might not be rejected (or it might), but a proposal
-of 15 pages definitely will. Similarly, the presentation at the start of
-the QE is required to be 1520 minutes. This will also be enforced. Both
-the written proposal and the oral presentation may include preliminary
-results if available but must address the whole of the projected thesis.
-- A successful QE will depend heavily on a top-quality proposal. This
-proposal should go through multiple drafts and be honed to a very finely
-worded document that shows the clarity of your thinking through
-conciseness and exact statements. Some topics you should probably cover
-are listed below. We recommend discussing omissions from this list with
-your advisor and your supervisory committee if you think some of these
-sections are not relevant to your particular project. - Brief review of
-the current state of knowledge - Precise statement of the question
-and/or hypotheses - Description of the methods - Detailed description of
-the experimental or sample design. Be clear about what factors are being
-controlled or sampled. Provide specific numbers for how many levels of
-each factor are planned, and how many replicates/samples within each
-factor. Address any issues that arise from finite effort levels in terms
-of tradeoffs between replication within vs.~between factors
-(i.e.~describe why your plan is optimal). Provide a realistic estimate
-of the amount of time this will require in the lab or field. -
-Statistical analysis approach. Describe specific statistical approaches,
-the output of these approaches, how these can be used to test your
-hypotheses, assumptions of the tests, and potential problems. - If you
-will be using novel measurement techniques, provide a detailed
-description (if you are using standard techniques then references to the
-standard techniques are enough). - Provide a description of each chapter
-anticipated in the dissertation (this - may be incorporated into the
-above sections or as a separate section). - A brief statement of the
-broader importance of the question to your field and to society -
-Provide a timeline showing when the research and writing will be
-performed
-\end{quote}
+We have some goal state for the future, and some estimate of what the
+state of the world will be given a set of actions.
+
+Brief summary of decision theory.
+
+Transition to theme of optimization given unknown information. In face
+of uncertainty, decision making is an optimization problem.
+
+\hypertarget{ch1-optimizing-sampling-of-species-distributions}{%
+\section{CH1 optimizing sampling of species
+distributions}\label{ch1-optimizing-sampling-of-species-distributions}}
+
+\begin{itemize}
+\tightlist
+\item
+  simulate species distribution and efficacy of detection given a set of
+  observation points where the dist from observation site decays.
+\item
+  optimize set of repeated sampling locations L for a \emph{known}
+  distribution D.
+\item
+  address SDM not being the territory
+\end{itemize}
+
+\hypertarget{ch2-optimizing-sampling-of-interactions}{%
+\section{CH2 optimizing sampling of
+interactions}\label{ch2-optimizing-sampling-of-interactions}}
+
+\begin{itemize}
+\tightlist
+\item
+  the missing link paper, turn this into optimizing with two different
+  SDMs
+\end{itemize}
+
+\hypertarget{ch3-optimizing-corridor-placement}{%
+\section{CH3 optimizing corridor
+placement}\label{ch3-optimizing-corridor-placement}}
+
+\begin{itemize}
+\tightlist
+\item
+  land cover -\textgreater{} resistance -\textgreater{} extinction time
+\item
+  simulated annealing to optimize landscape optimization
+\end{itemize}
+
+\hypertarget{ch4-a-software-note-on-the-resulting-packages.}{%
+\section{CH4 a software note on the resulting
+packages.}\label{ch4-a-software-note-on-the-resulting-packages.}}
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{Observatories.jl}, \texttt{Corridors.jl}, \texttt{MCD.jl}
+\end{itemize}
 

### 2021-10-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c3958339ff323180e7e2ff4617d752100d74ac9f 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@6c9053330422f4b3622416e17c37af0e447b7b55 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@bbdcc5611f22bf276b9d7a4ea2878d6145bf92b9 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
+{\Large\bfseries\sffamily Thesis proposal}
 \vskip 5em
@@
 \vfill
-
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+The proposal for my thesis, \emph{Simulation models for predictive
+ecology}
 
@@
 
-Forecasting in ecology.
-
-Forecasting in weather, introduce computers.
+Forecasting in ecology. Forecasting in weather, introduce computers.
 
@@
 Transition to theme of optimization given unknown information. In face
-of uncertainty, decision making is an optimization problem.
+of uncertainty, decision making is an optimization problem. Frame
+optimization problem mathematically an introduce concept of
+solution-space and constraint.
+
+Transition to how this is applied in ecology. Introduce idea of
+monitoring network. Transition to specifics of this thesis.
+
+\begin{figure}
+\centering
+\includegraphics{./figures/thesisconcept.png}
+\caption{thesis concept}
+\end{figure}
 
@@
 distributions}\label{ch1-optimizing-sampling-of-species-distributions}}
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
 
@@
 interactions}\label{ch2-optimizing-sampling-of-interactions}}
+
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
 

### 2021-10-05 preprint.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c3958339ff323180e7e2ff4617d752100d74ac9f 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@6c9053330422f4b3622416e17c37af0e447b7b55 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@bbdcc5611f22bf276b9d7a4ea2878d6145bf92b9 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
-manuscripts using markdown and github actions}}}
+\noindent {\LARGE \textbf{\textsf{Thesis proposal}}}
 
@@
 
-        {\bfseries Purpose:}\,This template provides a series of scripts
-to render a markdown document into an interactive website and a series
-of PDFs.\\%
-        {\bfseries Motivation:}\,It makes collaborating on text with
-GitHub easier, and means that we never need to think about the
-output.\\%
-        {\bfseries Internals:}\,GitHub actions and a series of python
-scritpts. The markdown is handled with \texttt{pandoc}.\\%
+The proposal for my thesis, \emph{Simulation models for predictive
+ecology}
 

### 2021-11-09 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@349e86c3239fa6571cd61d1d2d8acc077b7b54b1 🚀

@@
 
-Forecasting in ecology. Forecasting in weather, introduce computers.
+Within the last several hundred years, human activity has rapidly
+reshaped both Earth's surface. These changes can roughly be divided into
+two categories: (1) Land-use change, which has rapidly reshaped our
+planet's surface and restructured habitats for every species, and (2)
+climate change, words here, as a result of greenhouse gas emissions. As
+a result \emph{ecological forecasting} (\textbf{dietze?}), or modeling
+how ecological systems will change over time, has as an imperative to
+mitigate the effect of these changes on Earth's ecosystems, their
+functioning, and the services they provide to humans.
 
-Future is uncertain, how do we best act given a forecast?
+An oft applied definition of the origin of ecology is ``the application
+of the scientific method to natural history.'' Since its origin ecology
+has been a descriptive science. This is a natural biproduct of the
+immense variability of Earth's biosphere.
 
-We have some goal state for the future, and some estimate of what the
-state of the world will be given a set of actions.
+In recent years, there has been an interest in an epistemological shift
+in ecology. emerged to explain particular phenomena at particular
+scales.
 
-Brief summary of decision theory.
+To shift ecology into a predictive science. The justification for this
+shift is twofold: (1) bogged down philosophy of science, by further
+rooting our understanding of ecosystem function and dynamics in an
+ability to predict their structure (\textbf{PredictiveEcology?}). and
+(2) the practical need for models for \emph{ecological forecasting}.
 
-Transition to theme of optimization given unknown information. In face
-of uncertainty, decision making is an optimization problem. Frame
-optimization problem mathematically an introduce concept of
-solution-space and constraint.
+This term implicitly creates an analogy between predicting how
+ecosystems will change in the future and weather forecasting. Use of
+computational methods in NWP. Much as one would not aim to forecast the
+weather to Quebec by applying Navier-Stokes. NWP has worked because it
+incorporates information about data and meteorological processes
+collected at difference scales into models that.
 
-Transition to how this is applied in ecology. Introduce idea of
-monitoring network. Transition to specifics of this thesis.
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+Historically the term ``theory,'' as applied in the physical sciences,
+refers to mathematical models. Many (although not all) of these models
+refers to a equation describing how the value of an observable state of
+the system,
+\(\begin{bmatrix}x_1 \\ x_2 \\ \vdots \end{bmatrix} = \vec{x}\), changes
+as a function of time.
+
+differential equations (in continuous time, difference equations for
+discrete time)
+
+Ecological processes vary across more variables than the tools of
+analytic models are suited for. As the number of variables in an
+analytic model increases, so does the ability of the scientist to decern
+clear relationships between them. Chaotic dynamics emerge from simple
+analytic models, and .
+
+Whether ecosystems actually exhibit chaotic behavior is a different
+question.
+
+Until the 20th century, no theory of the gravitational dynamics of more
+than 2 bodies. Understanding the gravitational dynamics of more than two
+planets with any reliability proved difficult. Using the same models
+(diffeqs), how could we adaquetly predict ecosystems?
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+Transition to theme of optimization given unknown information. A
+forecast gives us a range of future values with uncertainty around them.
+Further a convenient property that a forecasting model's uncertainty
+goes up over time (if we assume the underlying process is Markov--this
+is a strong assumption but oft true of the models we fit to temporal
+data)
+
+In face of uncertainty, decision making is an optimization problem. We
+have some goal state for the future, and some estimate of what the state
+of the world will be given a set of actions. Frame optimization problem
+mathematically an introduce concept of solution-space and constraint.
+
+Indeed Marx's most well known quote that ``philosophers have hitherto
+only interpreted the world in various ways; the point is to change it.''
+
+and a necessary step toward establishing a just and sustainable world.
+
+Transition to specifics of this thesis.
 
@@
 
-\hypertarget{ch1-optimizing-sampling-of-species-distributions}{%
-\section{CH1 optimizing sampling of species
-distributions}\label{ch1-optimizing-sampling-of-species-distributions}}
+\hypertarget{ch1-forecasting-the-phenological-uncoupling-of-a-plant-pollinator-network}{%
+\section{CH1 Forecasting the phenological uncoupling of a
+plant-pollinator
+network}\label{ch1-forecasting-the-phenological-uncoupling-of-a-plant-pollinator-network}}
+
+This chapter uses several years of data on bee-flower phenology and
+interactions, combined with spatial records of species occurrence via
+GBIF, to predict the probability of each realized interaction network as
+a function of location and time.
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
 
@@
 
+\hypertarget{preliminary-results}{%
+\subsection{Preliminary Results}\label{preliminary-results}}
+
+Transition to next chapter by discussing uncertainty in interaction
+prediction across space.
+
 \hypertarget{ch2-optimizing-sampling-of-interactions}{%
@@
 interactions}\label{ch2-optimizing-sampling-of-interactions}}
+
+This chapter discusses the effect of species relative abundance on
+samples of interaction data, and proposes a method for optimizing
+spatial sampling of a possible interaction between species as a function
+of the estimated distribution of both species.
 
@@
 
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
 \hypertarget{ch3-optimizing-corridor-placement}{%
@@
 placement}\label{ch3-optimizing-corridor-placement}}
+
+This chapter proposes an algorithm for optimizing
+(corridorplacement/restoration effort) given a raster where each cell
+indicates land-cover. The optimization method uses the result of a
+simulated process (specifically occupancy dynamics in the landscape) and
+uses simulated annealing to estimate the global optimum of the
+targetstate (specfically mean-time-to-extinction for the occupancy
+dynamics example).
+
+\hypertarget{methods-2}{%
+\section{Methods}\label{methods-2}}
 
@@
 
+(MetacommunityDynamics.jl: a virtual laboratory for community ecology):
+a collection of modules in the Julia language for different aspects of
+metacommunity ecology, including most of the code used for the preceding
+chapters.
+
 \begin{itemize}
-\tightlist
+\item
+  TK conceptual figure with interfaces between what I'm writing / have
+  contributed to and linked with other libraries
 \item

### 2021-11-13 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c8118ede5a7a84925c6213b30f3a8c47fb6759e7 🚀

@@
 Within the last several hundred years, human activity has rapidly
-reshaped both Earth's surface. These changes can roughly be divided into
-two categories: (1) Land-use change, which has rapidly reshaped our
-planet's surface and restructured habitats for every species, and (2)
-climate change, words here, as a result of greenhouse gas emissions. As
-a result \emph{ecological forecasting} (\textbf{dietze?}), or modeling
-how ecological systems will change over time, has as an imperative to
-mitigate the effect of these changes on Earth's ecosystems, their
-functioning, and the services they provide to humans.
+reshaped Earth's surface. These changes can roughly be divided into two
+categories: (1) Land-use change, where Earth's surface changes and (2)
+climate change, words here, as a result of greenhouse gas emissions.
+
+As a result \emph{ecological forecasting} (\textbf{dietze?}), or
+modeling how ecological systems will change over time, has as an
+imperative to mitigate the effect of these changes on Earth's
+ecosystems, their functioning, and the services they provide to humans.
 
@@
 
+emerged to explain particular phenomena at particular scales.
+
 In recent years, there has been an interest in an epistemological shift
-in ecology. emerged to explain particular phenomena at particular
-scales.
-
-To shift ecology into a predictive science. The justification for this
-shift is twofold: (1) bogged down philosophy of science, by further
-rooting our understanding of ecosystem function and dynamics in an
-ability to predict their structure (\textbf{PredictiveEcology?}). and
-(2) the practical need for models for \emph{ecological forecasting}.
+in ecology. To shift ecology into a predictive science. The
+justification for this shift is twofold: (1) bogged down philosophy of
+science, by further rooting our understanding of ecosystem function and
+dynamics in an ability to predict their structure
+(\textbf{PredictiveEcology?}). and (2) the practical need for models for
+\emph{ecological forecasting}.
 

### 2021-11-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@d9eb006258265857374832c5e6edb4e2cad11213 🚀

@@
 
-As a result \emph{ecological forecasting} (\textbf{dietze?}), or
-modeling how ecological systems will change over time, has as an
+As a result \emph{ecological forecasting}, or building models to
+estimate how ecological systems will change over time, has as an
 imperative to mitigate the effect of these changes on Earth's
-ecosystems, their functioning, and the services they provide to humans.
+ecosystems, their functioning, and the services they provide to humans
+(\textbf{dietze?}).
 
-An oft applied definition of the origin of ecology is ``the application
-of the scientific method to natural history.'' Since its origin ecology
-has been a descriptive science. This is a natural biproduct of the
-immense variability of Earth's biosphere.
-
-emerged to explain particular phenomena at particular scales.
+An oft applied definition of the origin of is ``the application of the
+scientific method to natural history.'' Since its origin ecology has
+been a descriptive science. This is a natural by-product of the immense
+variability of Earth's biosphere. emerged to explain particular
+phenomena at particular scales.
 
@@
 
-This term implicitly creates an analogy between predicting how
-ecosystems will change in the future and weather forecasting. Use of
-computational methods in NWP. Much as one would not aim to forecast the
-weather to Quebec by applying Navier-Stokes. NWP has worked because it
-incorporates information about data and meteorological processes
-collected at difference scales into models that.
+Historically the term ``theory,'' as applied in the physical sciences,
+refers to mathematical models, typically an equation describing how the
+value of an observable state of the system, represented by a vector of
+numbers \([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time.
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+\(\vec{x}(t)\) but instead to define how the state of \(\vec{x}\)
+changes from one time to the next.
 
-Historically the term ``theory,'' as applied in the physical sciences,
-refers to mathematical models. Many (although not all) of these models
-refers to a equation describing how the value of an observable state of
-the system,
-\(\begin{bmatrix}x_1 \\ x_2 \\ \vdots \end{bmatrix} = \vec{x}\), changes
-as a function of time.
+Because of its early success in the physical science, the led to
+framework for bridging theory and data.
 
-differential equations (in continuous time, difference equations for
-discrete time)
+A large set of problems in ecology when aiming to confront
+high-dimensional analytic models with data:
+
+\begin{itemize}
+\tightlist
+\item
+  Often assume long-run equilibrium.
+\end{itemize}
 
 Ecological processes vary across more variables than the tools of
-analytic models are suited for. As the number of variables in an
-analytic model increases, so does the ability of the scientist to decern
-clear relationships between them. Chaotic dynamics emerge from simple
-analytic models, and .
+analytic models are suited for.
 
-Whether ecosystems actually exhibit chaotic behavior is a different
-question.
+As the number of variables in an analytic model increases, so does the
+ability of the scientist to decern clear relationships between them, and
+so does overfitting potential.
 
-Until the 20th century, no theory of the gravitational dynamics of more
-than 2 bodies. Understanding the gravitational dynamics of more than two
-planets with any reliability proved difficult. Using the same models
-(diffeqs), how could we adaquetly predict ecosystems?
+Curse of dimensionality--- Until the 20th century, no theory of the
+gravitational dynamics of more than 2 bodies. Understanding the
+gravitational dynamics of more than two planets with any reliability
+proved difficult. Using the same models (diffeqs), how could we
+adequately predict ecosystems?
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+Chaotic dynamics emerge from simple analytic models, and . Whether
+ecosystems actually exhibit chaotic behavior is a different question.
+
+The term \emph{ecological forecasting} implicitly creates an analogy
+between predicting how ecosystems will change in the future and weather
+forecasting. Use of computational methods in NWP. Much as one would not
+aim to forecast the weather in Quebec by applying Navier-Stokes. NWP has
+worked because it incorporates information about data and meteorological
+processes collected at difference scales into models that.
+
+Transition to simulation as the solution: shift toward approach of
+building models that \emph{generate} data.
+
+(resolving the semantic ambuity of what differentiates ``mechanistic''
+vs ``phenomological'' models is out of scope for now). ----
 
@@
 
-\hypertarget{ch1-forecasting-the-phenological-uncoupling-of-a-plant-pollinator-network}{%
-\section{CH1 Forecasting the phenological uncoupling of a
+\hypertarget{ch1-forecasting-the-spatial-and-phenological-uncoupling-of-a-plant-pollinator-network}{%
+\section{CH1 Forecasting the spatial and phenological uncoupling of a
 plant-pollinator
-network}\label{ch1-forecasting-the-phenological-uncoupling-of-a-plant-pollinator-network}}
+network}\label{ch1-forecasting-the-spatial-and-phenological-uncoupling-of-a-plant-pollinator-network}}
 
@@
 
+Two ways in which this network of interactions can become uncoupled:
+spatial and temporal. Overlap in ranges and shifts in ranges.
+Elevational gradient as proxy for range shifts
+
 \hypertarget{data}{%
 \subsection{Data}\label{data}}
+
+System description: lots of data on \emph{Bombus} (bumblebees) and
+wildflowers. Three different sites, (7/7/3) years each, each covering an
+elevational gradient.
 
@@
 
-\begin{itemize}
+Split the process into parts.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
 \tightlist
 \item
-  simulate species distribution and efficacy of detection given a set of
-  observation points where the dist from observation site decays.
+  Building an interaction prediction model.
 \item
-  optimize set of repeated sampling locations L for a \emph{known}
-  distribution D.
+  Make it spatial based on distributions.
 \item
-  address SDM not being the territory
-\end{itemize}
+  Forecast distributions based on CMIP6.
+\end{enumerate}
 
@@
 \begin{itemize}
-\tightlist
 \item
@@
   SDMs
+\item
+  relative abundance and its effect on false negative
+\item
+  non-independent associations in samples
+\item
+  simulate species distribution and efficacy of detection given a set of
+  observation points where the dist from observation site decays.
+\item
+  optimize set of repeated sampling locations L for a \emph{known}
+  distribution D.
+\item
+  address SDM not being the territory
 \end{itemize}

### 2021-11-14 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@988ab764fd8e5bae8d99ac2200bddea12f7d3be8 🚀

@@
 
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
 Within the last several hundred years, human activity has rapidly
@@
 ecosystems, their functioning, and the services they provide to humans
-(\textbf{dietze?}).
+(Dietze 2017).
 
@@
 science, by further rooting our understanding of ecosystem function and
-dynamics in an ability to predict their structure
-(\textbf{PredictiveEcology?}). and (2) the practical need for models for
-\emph{ecological forecasting}.
+dynamics in an ability to predict their structure (Dietze 2017). and (2)
+the practical need for models for \emph{ecological forecasting}.
 
@@
 
-\begin{itemize}
-\tightlist
-\item
 Often assume long-run equilibrium.
-\end{itemize}
 
@@
 \hypertarget{methods-2}{%
-\section{Methods}\label{methods-2}}
+\subsection{Methods}\label{methods-2}}
 
@@
 
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Dietze2017PreEco}{}%
+Dietze, M.C. (2017). Prediction in ecology: A first-principles
+framework. \emph{Ecological Applications}, 27, 2048--2060.
+
+\end{CSLReferences}
+
 \end{document}

### 2021-11-14 preprint.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e17d4b3558edbbf2dd2bac83be78caa81bd7ebec 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@988ab764fd8e5bae8d99ac2200bddea12f7d3be8 🚀

@@
 \vskip 1em
-\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences\\
-\vskip 1em
-\textbf{Correspondance to:}\\
-Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
-}
 \end{flushleft}
@@
 
-\marginpar{\vskip 1em\flushright
-{\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
-}
-
 The proposal for my thesis, \emph{Simulation models for predictive
@@
 \vskip 2em
+
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 

### 2021-11-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@1c0ec0db4683880291e720b0d407cbc02cfc9d64 🚀

@@
 
-Within the last several hundred years, human activity has rapidly
-reshaped Earth's surface. These changes can roughly be divided into two
-categories: (1) Land-use change, where Earth's surface changes and (2)
-climate change, words here, as a result of greenhouse gas emissions.
+\begin{longtable}[]{@{}l@{}}
+\toprule
+\endhead
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+\textbf{P1}\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+Within the last several hundred years, human activity have rapidly
+changed Earth's atmosphere, oceans, and surface. Greenhouse gas
+emissions have caused an increase the temperature of both Earth's
+surface and oceans (resulting in acidification), and both agricultural
+and urban development has rapidly reshaped Earth's surface. These the
+bulk of this change has occurred within the last several hundred years,
+a geological instant, potentially inducing shocks to ecosystems that
+could threated their integrity (\textbf{Scheffer?}). As a result
+understanding and predicting how ecosystems will change in the future,
+\emph{ecological forecasting}, and making making descisions based on
+these predictions mitigating the consequences of this change, on
+ecosystems has emerged as an imperative for ecology and environmental
+science {[}Dietze (2017);{]}.\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
 
-As a result \emph{ecological forecasting}, or building models to
-estimate how ecological systems will change over time, has as an
-imperative to mitigate the effect of these changes on Earth's
-ecosystems, their functioning, and the services they provide to humans
-(Dietze 2017).
+\textbf{P2}
 
-An oft applied definition of the origin of is ``the application of the
-scientific method to natural history.'' Since its origin ecology has
-been a descriptive science. This is a natural by-product of the immense
-variability of Earth's biosphere. emerged to explain particular
-phenomena at particular scales.
+However, robust forecasting of ecological processes will change in the
+future is, to say the least, quite difficult. This difficultly is
+compounded by a few factors, the first being that sampling ecosystems is
+not easy. Ecological data is often biased, and noisey, spatially and
+temporally sparse. As a result \emph{ecosystem monitoring} (Makiola
+\emph{et al.} 2020) has emerged as an imperative. Developing a system
+for ecological observation, which is able to coordinate across
+locations. (\textbf{AndyUrbanBiomonitoring?} paper).
 
-In recent years, there has been an interest in an epistemological shift
-in ecology. To shift ecology into a predictive science. The
-justification for this shift is twofold: (1) bogged down philosophy of
-science, by further rooting our understanding of ecosystem function and
-dynamics in an ability to predict their structure (Dietze 2017). and (2)
-the practical need for models for \emph{ecological forecasting}.
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
-Historically the term ``theory,'' as applied in the physical sciences,
-refers to mathematical models, typically an equation describing how the
-value of an observable state of the system, represented by a vector of
-numbers \([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time.
+The second major challenge in forecasting ecosystems is that the
+underlying dynamics of most ecological processes are fundementally
+unknown (and unknowable) and instead must be inferred.
 
-\(\vec{x}(t)\) but instead to define how the state of \(\vec{x}\)
-changes from one time to the next.
+Much of the history of quantitatively modeling ecosystems have been done
+in the language of dynamical systems, describing how the value of an
+observable state of the system, represented by a vector of numbers
+\([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time. It turns
+out to be much more effective to, rather than attempt to directly model
+\(\vec{x}(t)\) itself, to instead describe how \(\vec{x}\) changes from
+one timestep to the next, yielding models in the form of differential
+equations in continuous-time settings--\(\frac{dx}{dt} = f(x)\)-- or
+difference equations in discrete-time
+settings---\(x_t = f(x_{t-1})\)---where
+\(f:\mathbb{R}^n \to \mathbb{R}^n\) is an arbitrary function describing
+how the system changes on a moment-to-moment basis (e.g.~in the context
+of communities, \(f\) could be Lotka-Voltera, Holling-Type-III or
+DeAngelis-Beddington functional response). The form of this functional
+response in real systems is effectively unknown, and some forms are
+inherently more ``forecastable'' than others (Chen \emph{et al.} 2019).
 
-Because of its early success in the physical science, the led to
-framework for bridging theory and data.
-
-A large set of problems in ecology when aiming to confront
-high-dimensional analytic models with data:
-
-Often assume long-run equilibrium.
-
-Ecological processes vary across more variables than the tools of
-analytic models are suited for.
-
-As the number of variables in an analytic model increases, so does the
-ability of the scientist to decern clear relationships between them, and
-so does overfitting potential.
-
+\begin{longtable}[]{@{}l@{}}
+\toprule
+\endhead
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+\textbf{P3}\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+However, we run into many problems when aiming to apply this type of
+model to empirical data in ecology.\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+The initial success of ODE models can be traced back to the larger
+program of ontological reductionism, which became the de facto apporoach
+model physical sciences after its early success in physics, which, and
+by the time ecology was becoming a quantitative science (sometime in the
+20th century, depending on who you ask), became the foundation for early
+quantitative models in ecology.\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+But ecosystems are perhaps the quintessential example of system that
+cannot be understood simply by iterative reduction of its components.
+Emergent phenomena, mechanisms at different scales, etc.\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+Some have been explored in the ecological literature: (1) Some
+applications of dynamic models in ecology assume long-run equilibrium.
+(2) Stochasticity\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.05\columnwidth}\raggedright
+(3) Ecological processes vary across more variables than the tools of
+analytic models are suited for. As the number of variables in an
+analytic model increases, so does the ability of the scientist to decern
+clear relationships between them, and so does overfitting potential.
 Curse of dimensionality--- Until the 20th century, no theory of the
@@
 proved difficult. Using the same models (diffeqs), how could we
-adequately predict ecosystems?
+adequately predict ecosystems?\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
 
-Chaotic dynamics emerge from simple analytic models, and . Whether
-ecosystems actually exhibit chaotic behavior is a different question.
+\emph{P4}
 
 The term \emph{ecological forecasting} implicitly creates an analogy
-between predicting how ecosystems will change in the future and weather
-forecasting. Use of computational methods in NWP. Much as one would not
-aim to forecast the weather in Quebec by applying Navier-Stokes. NWP has
-worked because it incorporates information about data and meteorological
-processes collected at difference scales into models that.
+between predicting how ecosystems will change in the future by using the
+term ``forecasting''---the most immediate analog is the success story of
+forecasting is numerical weather prediction (NWP;
+\textbf{Bauer2015QuiRev?}).
+
+Much like ecology, NWP is faced with high-dimensional systems that are
+governed by different mechanisms at different scales.
+
+Much as one would not aim to forecast the weather in Quebec by applying
+Navier-Stokes. NWP has worked because it incorporates information about
+data and meteorological processes collected at difference scales into
+models that. Use of computational methods in NWP.
 
@@
 (resolving the semantic ambuity of what differentiates ``mechanistic''
-vs ``phenomological'' models is out of scope for now). ----
+vs ``phenomological'' models is out of scope for now).
+
+More broadly a reflection reflect ecology lagging behind the statistical
+methods used in sciences that face similar challenges (many dimensions,
+many mechanisms at different scales, each with stochasticity). Chaotic
+dynamics emerge from simple analytic models, and . Whether ecosystems
+actually exhibit chaotic behavior is a different question.
+
+\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
+
+\textbf{P5}
+
+But forecasting isn't the only difficult problem here.
 
@@
 
-\hypertarget{ch1-forecasting-the-spatial-and-phenological-uncoupling-of-a-plant-pollinator-network}{%
-\section{CH1 Forecasting the spatial and phenological uncoupling of a
+\hypertarget{chapter-one-forecasting-the-spatial-uncoupling-of-a-plant-pollinator-network}{%
+\section{Chapter One: Forecasting the spatial uncoupling of a
 plant-pollinator
-network}\label{ch1-forecasting-the-spatial-and-phenological-uncoupling-of-a-plant-pollinator-network}}
+network}\label{chapter-one-forecasting-the-spatial-uncoupling-of-a-plant-pollinator-network}}
+
+Plants and pollinators form interaction networks, called the
+``architecture of biodiversity'' (\textbf{Jordano2007?}).
+
+The stability, function, and persistance of ecosystems relies on the
+structure of these interactions. Antropogenic change threatens to
+unravel these networks. Two aspects to this change: spatial and
+temporal. Spatially, range shifts along elevational gradient, and
+temporall, phenological shifts.
+
+The issue is that we don't really know what interactions are like now.
+So not only do we need to predict with data that is spatially and
+temporally sparse and likely to contain many interaction
+``false-negatives'' (\textbf{Strydom2021?})
 
@@
 interactions, combined with spatial records of species occurrence via
-GBIF, to predict the probability of each realized interaction network as
-a function of location and time.
+GBIF, to forecast how much overlap there will be between
+plants/pollinators in space/time.
 
-Two ways in which this network of interactions can become uncoupled:
-spatial and temporal. Overlap in ranges and shifts in ranges.
-Elevational gradient as proxy for range shifts
+In stages, (1) take data from multiple sites to predict a spatial
+metaweb of \emph{Bombus}-flower interactions across Colorado. (2)
+Predict how these spatial distributions will change under CMIP6. and (3)
+quantify the lack of overlap between species for which there is a
+predicted
+
+\textbf{CH1 concept figure}
 
@@
 
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  we got a tree
+\end{enumerate}
+
 Transition to next chapter by discussing uncertainty in interaction
@@
 
-This chapter discusses the effect of species relative abundance on
-samples of interaction data, and proposes a method for optimizing
-spatial sampling of a possible interaction between species as a function
-of the estimated distribution of both species.
+This chapter quantifies the relationship between a given species
+relative abundance and the sampling effort needed to adequately
+understand this species distribution and interactions.
+
+For a given sample of interaction data, and proposes a method for
+optimizing spatial sampling of a possible interaction between species as
+a function of the estimated distribution of both species.
 
@@
 
+\hypertarget{in-progress-results}{%
+\subsubsection{In-progress results}\label{in-progress-results}}
+
 \hypertarget{ch3-optimizing-corridor-placement}{%
@@
 
-This chapter proposes an algorithm for optimizing
+This chapter proposes an algorithm for optimizing restoration across
+space
+
 (corridorplacement/restoration effort) given a raster where each cell
@@
 
+\hypertarget{concl}{%
+\section{concl}\label{concl}}
+
+// this is a discussion para An oft applied definition of the origin of
+is ``the application of the scientific method to natural history.''
+Since its origin ecology has been a descriptive science. This is a
+natural by-product of the immense variability of Earth's biosphere.
+emerged to explain particular phenomena at particular scales. In recent
+years, there has been an interest in an epistemological shift in
+ecology. To shift ecology into a predictive science. The justification
+for this shift is twofold: (1) bogged down philosophy of science, by
+further rooting our understanding of ecosystem function and dynamics in
+an ability to predict their structure (Dietze 2017). and (2) the
+practical need for models for \emph{ecological forecasting}.
+
 \hypertarget{references}{%
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Chen2019RevCom}{}%
+Chen, Y., Angulo, M.T. \& Liu, Y.-Y. (2019). Revealing Complex
+Ecological Dynamics via Symbolic Regression. \emph{BioEssays}, 41,
+1900069.
+
 \leavevmode\hypertarget{ref-Dietze2017PreEco}{}%
@@
 
+\leavevmode\hypertarget{ref-Makiola2020KeyQue}{}%
+Makiola, A., Compson, Z.G., Baird, D.J., Barnes, M.A., Boerlijst, S.P.,
+Bouchez, A., \emph{et al.} (2020). Key Questions for Next-Generation
+Biomonitoring. \emph{Frontiers in Environmental Science}, 7.
+
 \end{CSLReferences}

### 2021-11-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@1f6ad5231268fff67c553a94829210342d470c00 🚀

@@
 between predicting how ecosystems will change in the future by using the
-term ``forecasting''---the most immediate analog is the success story of
-forecasting is numerical weather prediction (NWP;
-\textbf{Bauer2015QuiRev?}).
+term ``forecasting''---the most immediate analog being the success story
+of weather forecasting via numerical weather prediction (NWP).
 
-Much like ecology, NWP is faced with high-dimensional systems that are
-governed by different mechanisms at different scales.
+Although it is become almost hack to complain about the dang weather
+forecast being wrong, over the least 50 years the
+(\textbf{Bauer2015QuiRev?}).
+
+The success of NWP, and the Earth observations that support it should
+serve as a template for development of a system for monitoring Earth's
+biodiversity. Much like ecology, NWP is faced with high-dimensional
+systems that are governed by different mechanisms at different scales.
 
@@
 
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
-
-\textbf{P5}
-
-But forecasting isn't the only difficult problem here.
-
+\begin{longtable}[]{@{}l@{}}
+\toprule
+\endhead
+\begin{minipage}[t]{0.07\columnwidth}\raggedright
+\textbf{P5}\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.07\columnwidth}\raggedright
+But forecasting isn't the only difficult problem here.\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.07\columnwidth}\raggedright
 Transition to theme of optimization given unknown information. A
@@
 is a strong assumption but oft true of the models we fit to temporal
-data)
-
+data)\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.07\columnwidth}\raggedright
 In face of uncertainty, decision making is an optimization problem. We
@@
 of the world will be given a set of actions. Frame optimization problem
-mathematically an introduce concept of solution-space and constraint.
-
+mathematically an introduce concept of solution-space and
+constraint.\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.07\columnwidth}\raggedright
 Indeed Marx's most well known quote that ``philosophers have hitherto
-only interpreted the world in various ways; the point is to change it.''
-
-and a necessary step toward establishing a just and sustainable world.
-
-Transition to specifics of this thesis.
+only interpreted the world in various ways; the point is to change
+it.''\strut
+\end{minipage}\tabularnewline
+\begin{minipage}[t]{0.07\columnwidth}\raggedright
+and a necessary step toward establishing a just and sustainable
+world.\strut
+\end{minipage}\tabularnewline
+\bottomrule
+\end{longtable}
 
 \begin{figure}
+\hypertarget{fig:thesis}{%
 \centering
 \includegraphics{./figures/thesisconcept.png}
-\caption{thesis concept}
+\caption{thesis concept}\label{fig:thesis}
+}
 \end{figure}
+
+\textbf{P6 -- final intro para}
+
+Three major components here: 1) Ecosystem monitoring, 2) Forecasting
+using the products of that monitoring, and 3) Choosing the best possible
+mitigation strategy.
+
+This flow is outlined in the left panel of fig.~\ref{fig:thesis}
 

### 2021-11-19 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@ef6926217c28fafceae6299e600a081ed616414b 🚀

--- 2021-11-19 draft.tex
@@
 
-\begin{longtable}[]{@{}l@{}}
-\toprule
-\endhead
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
-\textbf{P1}\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
-Within the last several hundred years, human activity have rapidly
+\textbf{P1}
+
+Within the last several hundred years, human activity has rapidly
 changed Earth's atmosphere, oceans, and surface. Greenhouse gas
 emissions have caused an increase the temperature of both Earth's
-surface and oceans (resulting in acidification), and both agricultural
-and urban development has rapidly reshaped Earth's surface. These the
+terrestial surface and its oceans, and both agricultural and urban
+development has rapidly reshaped the cover of Earth's surface. These the
 bulk of this change has occurred within the last several hundred years,
@@
 ecosystems has emerged as an imperative for ecology and environmental
-science {[}Dietze (2017);{]}.\strut
-\end{minipage}\tabularnewline
-\bottomrule
-\end{longtable}
+science {[}Dietze (2017);{]}.
 
@@
 locations. (\textbf{AndyUrbanBiomonitoring?} paper).
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 difference equations in discrete-time
-settings---\(x_t = f(x_{t-1})\)---where
+settings--\(x_t = f(x_{t-1})\)--where
 \(f:\mathbb{R}^n \to \mathbb{R}^n\) is an arbitrary function describing
@@
 
-\begin{longtable}[]{@{}l@{}}
-\toprule
-\endhead
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
-\textbf{P3}\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
+\textbf{P3}
+
 However, we run into many problems when aiming to apply this type of
-model to empirical data in ecology.\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
+model to empirical data in ecology.
+
 The initial success of ODE models can be traced back to the larger
@@
 20th century, depending on who you ask), became the foundation for early
-quantitative models in ecology.\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
+quantitative models in ecology.
+
 But ecosystems are perhaps the quintessential example of system that
 cannot be understood simply by iterative reduction of its components.
-Emergent phenomena, mechanisms at different scales, etc.\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
+Emergent phenomena, mechanisms at different scales, etc.
+
 Some have been explored in the ecological literature: (1) Some
 applications of dynamic models in ecology assume long-run equilibrium.
-(2) Stochasticity\strut
-\end{minipage}\tabularnewline
-\begin{minipage}[t]{0.05\columnwidth}\raggedright
-(3) Ecological processes vary across more variables than the tools of
+(2) Stochasticity
+
+\begin{enumerate}
+\def\labelenumi{(\arabic{enumi})}
+\setcounter{enumi}{2}
+\tightlist
+\item
+  Ecological processes vary across more variables than the tools of
   analytic models are suited for. As the number of variables in an
-analytic model increases, so does the ability of the scientist to decern
-clear relationships between them, and so does overfitting potential.
-Curse of dimensionality--- Until the 20th century, no theory of the
-gravitational dynamics of more than 2 bodies. Understanding the
-gravitational dynamics of more than two planets with any reliability
-proved difficult. Using the same models (diffeqs), how could we
-adequately predict ecosystems?\strut
-\end{minipage}\tabularnewline
-\bottomrule
-\end{longtable}
+  analytic model increases, so does the ability of the scientist to
+  decern clear relationships between them, and so does overfitting
+  potential. Curse of dimensionality--- Until the 20th century, no
+  theory of the gravitational dynamics of more than 2 bodies.
+  Understanding the gravitational dynamics of more than two planets with
+  any reliability proved difficult. Using the same models (diffeqs), how
+  could we adequately predict ecosystems?
+\end{enumerate}
 
-\emph{P4}
+\textbf{P4}
 
@@
 between predicting how ecosystems will change in the future by using the
-term ``forecasting''---the most immediate analog is the success story of
-forecasting is numerical weather prediction (NWP;
-\textbf{Bauer2015QuiRev?}).
+term ``forecasting''---the most immediate analog being the success story
+of weather forecasting via numerical weather prediction (NWP).
 
-Much like ecology, NWP is faced with high-dimensional systems that are
-governed by different mechanisms at different scales.
+Although it is become almost hack to complain about the dang weather
+forecast being wrong, over the least 50 years the
+(\textbf{Bauer2015QuiRev?}).
+
+The success of NWP, and the Earth observations that support it should
+serve as a template for development of a system for monitoring Earth's
+biodiversity. Much like ecology, NWP is faced with high-dimensional
+systems that are governed by different mechanisms at different scales.
+
+NWP has worked because it incorporates information about data and
+meteorological processes collected at difference scales into models
+that. Use of computational methods in NWP.
 
 Much as one would not aim to forecast the weather in Quebec by applying
-Navier-Stokes. NWP has worked because it incorporates information about
-data and meteorological processes collected at difference scales into
-models that. Use of computational methods in NWP.
+Navier-Stokes, forecasting ecological systems must
 
@@
 actually exhibit chaotic behavior is a different question.
-
-\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}
 
@@
 only interpreted the world in various ways; the point is to change it.''
-
 and a necessary step toward establishing a just and sustainable world.
 
-Transition to specifics of this thesis.
-
 \begin{figure}
+\hypertarget{fig:thesis}{%
 \centering
 \includegraphics{./figures/thesisconcept.png}
-\caption{thesis concept}
+\caption{thesis concept}\label{fig:thesis}
+}
 \end{figure}
+
+\textbf{P6 -- final intro para}
+
+Three major components here: 1) Ecosystem monitoring, 2) Forecasting
+using the products of that monitoring, and 3) Choosing the best possible
+mitigation strategy.
+
+This flow is outlined in the left panel of fig.~\ref{fig:thesis}
 
@@
 
+\hypertarget{appendix}{%
+\section{Appendix}\label{appendix}}
+
 \hypertarget{references}{%

### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@ae104464ff5a0ac19d1b58a70d83427601ec710a 🚀

@@
 However, robust forecasting of ecological processes will change in the
-future is, to say the least, quite difficult. This difficultly is
-compounded by a few factors, the first being that sampling ecosystems is
-not easy. Ecological data is often biased, and noisey, spatially and
-temporally sparse. As a result \emph{ecosystem monitoring} (Makiola
-\emph{et al.} 2020) has emerged as an imperative. Developing a system
-for ecological observation, which is able to coordinate across
-locations. (\textbf{AndyUrbanBiomonitoring?} paper).
+future is, to say the least, quite difficult (Beckage \emph{et al.}
+2011; Petchey \emph{et al.} 2015). This difficultly is compounded by a
+few factors, the first being that sampling ecosystems is not easy.
+Ecological data is often biased, and noisey, spatially and temporally
+sparse. As a result \emph{ecosystem monitoring} (Makiola \emph{et al.}
+2020) has emerged as an imperative. Developing a system for ecological
+observation, which is able to coordinate across locations.
+(\textbf{AndyUrbanBiomonitoring?} paper).
 
@@
 Although it is become almost hack to complain about the dang weather
-forecast being wrong, over the least 50 years the
-(\textbf{Bauer2015QuiRev?}).
+forecast being wrong, over the least 50 years the (Bauer \emph{et al.}
+2015).
 
@@
 
+The data for this chapter is derived from multiple souces and can be
+split into three categories. (1) Field data from three different
+locations acvross Colorado. All field sites have multiple plots across
+an elevational gradient.
+
 System description: lots of data on \emph{Bombus} (bumblebees) and
@@
 \item
-  Building an interaction prediction model.
-\item
-  Make it spatial based on distributions.
-\item
-  Forecast distributions based on CMIP6.
+  Building an interaction prediction model. 2) Make it spatial based on
+  distributions. 3) Forecast distributions based on CMIP6.
 \end{enumerate}
@@
 
-\hypertarget{ch2-optimizing-sampling-of-interactions}{%
-\section{CH2 optimizing sampling of
-interactions}\label{ch2-optimizing-sampling-of-interactions}}
+\hypertarget{chapter-two-optimizing-spatial-sampling-of-species-interactions}{%
+\section{Chapter Two: Optimizing spatial sampling of species
+interactions}\label{chapter-two-optimizing-spatial-sampling-of-species-interactions}}
 
-This chapter quantifies the relationship between a given species
-relative abundance and the sampling effort needed to adequately
-understand this species distribution and interactions.
+There are false-negatives in interation data. Co-occurrence is not the
+same thing as interaction (\textbf{cite?}), but often is used as a
+proxy.
 
-For a given sample of interaction data, and proposes a method for
-optimizing spatial sampling of a possible interaction between species as
-a function of the estimated distribution of both species.
+This chapter unravels the relationship between a given species relative
+abundance and the sampling effort needed to adequately understand this
+species distribution and interactions.
+
+There is more than one way to observe a false-negative.
+
+\begin{figure}
+\centering
+\includegraphics{./figures/ch2.png}
+\caption{taxonomy of false negatives}
+\end{figure}
 
@@
   the missing link paper, turn this into optimizing with two different
-  SDMs
-\item
-  relative abundance and its effect on false negative
-\item
+  SDMs relative abundance and its effect on false negative
   non-independent associations in samples
@@
   observation points where the dist from observation site decays.
-\item
   optimize set of repeated sampling locations L for a \emph{known}
-  distribution D.
-\item
-  address SDM not being the territory
+  distribution D. address SDM not being the territory
 \end{itemize}
@@
 \subsection{Results}\label{results}}
+
+\begin{itemize}
+\tightlist
+\item
+  nonrandom association figure sampling effort under neutral model
+\end{itemize}
 
@@
   land cover -\textgreater{} resistance -\textgreater{} extinction time
+  simulated annealing to
 \item
-  simulated annealing to optimize landscape optimization
+  optimize landscape optimization
 \end{itemize}
@@
   TK conceptual figure with interfaces between what I'm writing / have
+\item
   contributed to and linked with other libraries
@@
 
-\hypertarget{concl}{%
-\section{concl}\label{concl}}
-
-// this is a discussion para An oft applied definition of the origin of
-is ``the application of the scientific method to natural history.''
-Since its origin ecology has been a descriptive science. This is a
-natural by-product of the immense variability of Earth's biosphere.
-emerged to explain particular phenomena at particular scales. In recent
-years, there has been an interest in an epistemological shift in
-ecology. To shift ecology into a predictive science. The justification
-for this shift is twofold: (1) bogged down philosophy of science, by
-further rooting our understanding of ecosystem function and dynamics in
-an ability to predict their structure (Dietze 2017). and (2) the
-practical need for models for \emph{ecological forecasting}.
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
 
@@
 \section{Appendix}\label{appendix}}
+
+\begin{figure}
+\centering
+\includegraphics{./figures/trees.png}
+\caption{trees}
+\end{figure}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Bauer2015QuiRev}{}%
+Bauer, P., Thorpe, A. \& Brunet, G. (2015). The quiet revolution of
+numerical weather prediction. \emph{Nature}, 525, 47--56.
+
+\leavevmode\hypertarget{ref-Beckage2011LimPre}{}%
+Beckage, B., Gross, L.J. \& Kauffman, S. (2011). The limits to
+prediction in ecological systems. \emph{Ecosphere}, 2, art125.
+
 \leavevmode\hypertarget{ref-Chen2019RevCom}{}%
@@
 
+\leavevmode\hypertarget{ref-Petchey2015EcoFor}{}%
+Petchey, O.L., Pontarp, M., Massie, T.M., Kéfi, S., Ozgul, A.,
+Weilenmann, M., \emph{et al.} (2015). The ecological forecast horizon,
+and examples of its uses and determinants. \emph{Ecology Letters}, 18,
+597--611.
+
 \end{CSLReferences}

### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@c8ba22b8d2ce32a5b66db878c1d33e5f28831815 🚀

@@
 
-\hypertarget{ch3-optimizing-corridor-placement}{%
-\section{CH3 optimizing corridor
-placement}\label{ch3-optimizing-corridor-placement}}
+\hypertarget{chapter-three-optimizing-corridor-placement-against-ecological-dynamics}{%
+\section{Chapter Three: Optimizing corridor placement against ecological
+dynamics}\label{chapter-three-optimizing-corridor-placement-against-ecological-dynamics}}
+
+As human activity
 
@@
 chapters.
+
+\begin{figure}
+\centering
+\includegraphics{./figures/software.png}
+\caption{todo}
+\end{figure}
 

### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4dff9e279780e0c0c7206cc3db0fb63c0833faa6 🚀

@@
 program of ontological reductionism, which became the de facto apporoach
-model physical sciences after its early success in physics, which, and
-by the time ecology was becoming a quantitative science (sometime in the
+model physical sciences after its early success in physics, which, by
+the time ecology was becoming a quantitative science (sometime in the
 20th century, depending on who you ask), became the foundation for early
@@
 
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
+It begins with a conceptual framework for understanding the difference
+in false-negatives in occurrence, co-occurrence, and interactions
+(fig.~3). We use a null model of the relative-abundance distribution
+(Hubbell 2001) to simulate realized false-negatives as a function of
+varying sampling effort.
 
-\begin{itemize}
-\item
-  the missing link paper, turn this into optimizing with two different
-  SDMs relative abundance and its effect on false negative
-  non-independent associations in samples
-\item
-  simulate species distribution and efficacy of detection given a set of
-  observation points where the dist from observation site decays.
-  optimize set of repeated sampling locations L for a \emph{known}
+This also goes on to includes testing some assumptions of the model with
+empirical data fig.~\ref{fig:4}. which indicate our neutral model, if
+anything, underestimates the probability of false-negatives due to
+positive correlations in co-occurrence in two spatially replicated
+networks (Thompson \& Townsend 2000; Hadfield \emph{et al.}
+2014)---further I'm planning to add the field data from chapter one into
+this anlysis once complete.
+
+\begin{figure}
+\centering
+\includegraphics{./figures/positiveassociations.png}
+\caption{f}
+\end{figure}
+
+new addition: - simulate species distribution and efficacy of detection
+given a set of observation points where the dist from observation site
+decays. optimize set of repeated sampling locations L for a \emph{known}
 distribution D. address SDM not being the territory
-\end{itemize}
 
@@
 
-\hypertarget{in-progress-results}{%
-\subsubsection{In-progress results}\label{in-progress-results}}
-
 \hypertarget{chapter-three-optimizing-corridor-placement-against-ecological-dynamics}{%
@@
 
-As human activity
+Promoting landscape connectivity is important to mitigate the effects of
+land-use change on Earth's biodiversity. However, the practical
+realities of conservation mean that there is a limitation on how much we
+can modify landscapes in order to do this. So what is the best place to
+put a corridor given a constraint on how much surface-area you can
+change in a landscape? This is the question this chapter seeks to
+answer. Models for proposing corridor locations have been developed, but
+are limited in that are not developed around promoting some element of
+ecosystem function, but instead by trying to find the path of least
+resistance given a resistance surface (Peterman 2018).
 
-This chapter proposes an algorithm for optimizing restoration across
-space
+This chapter proposes a general algorithm for optimizing corridor
+placement based on a measurement of ecosystem functioning derived from
+simulations run on a proposed landscape modification. We propose various
+landscape modifications which alter the cover of a landscape,
+represented as a raster (fig.~6, left). We then compute a new resistance
+surface based on the proposed landscape modification, and based on the
+values of resistance to dispersal between each location we simulate
+spatially-explicit metapopulation dynamics model (Hanski \& Ovaskainen
+2000; Ovaskainen \emph{et al.} 2002) to estimate a distribution of time
+until extinction for each landscape modification (fig.~6, right).
 
-(corridorplacement/restoration effort) given a raster where each cell
-indicates land-cover. The optimization method uses the result of a
-simulated process (specifically occupancy dynamics in the landscape) and
-uses simulated annealing to estimate the global optimum of the
-targetstate (specfically mean-time-to-extinction for the occupancy
-dynamics example).
-
-\hypertarget{methods-2}{%
-\subsection{Methods}\label{methods-2}}
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
 
@@
 \end{figure}
-
-\begin{itemize}
-\item
-  TK conceptual figure with interfaces between what I'm writing / have
-\item
-  contributed to and linked with other libraries
-\item
-  \texttt{Observatories.jl}, \texttt{Corridors.jl}, \texttt{MCD.jl}
-\end{itemize}
 
@@
 
+\leavevmode\hypertarget{ref-Hadfield2014TalTwo}{}%
+Hadfield, J.D., Krasnov, B.R., Poulin, R. \& Nakagawa, S. (2014). A Tale
+of Two Phylogenies: Comparative Analyses of Ecological Interactions.
+\emph{The American Naturalist}, 183, 174--187.
+
+\leavevmode\hypertarget{ref-Hanski2000MetCap}{}%
+Hanski, I. \& Ovaskainen, O. (2000). The metapopulation capacity of a
+fragmented landscape. \emph{Nature}, 404, 755--758.
+
+\leavevmode\hypertarget{ref-Hubbell2001UniNeu}{}%
+Hubbell, S.P. (2001). \emph{The unified neutral theory of biodiversity
+and biogeography}. Monographs in population biology. Princeton
+University Press, Princeton.
+
 \leavevmode\hypertarget{ref-Makiola2020KeyQue}{}%
@@
 Biomonitoring. \emph{Frontiers in Environmental Science}, 7.
+
+\leavevmode\hypertarget{ref-Ovaskainen2002MetMod}{}%
+Ovaskainen, O., Sato, K., Bascompte, J. \& Hanski, I. (2002).
+Metapopulation Models for Extinction Threshold in Spatially Correlated
+Landscapes. \emph{Journal of Theoretical Biology}, 215, 95--108.
+
+\leavevmode\hypertarget{ref-Ovaskainen2002MetMod}{}%
+Ovaskainen, O., Sato, K., Bascompte, J. \& Hanski, I. (2002).
+Metapopulation Models for Extinction Threshold in Spatially Correlated
+Landscapes. \emph{Journal of Theoretical Biology}, 215, 95--108.
 
@@
 
+\leavevmode\hypertarget{ref-Peterman2018ResRP}{}%
+Peterman, W.E. (2018). ResistanceGA: An R package for the optimization
+of resistance surfaces using genetic algorithms. \emph{Methods in
+Ecology and Evolution}, 9, 1638--1647.
+
+\leavevmode\hypertarget{ref-Thompson2000ResSol}{}%
+Thompson, R.M. \& Townsend, C.R. (2000). Is resolution the solution?:
+The effect of taxonomic resolution on the calculated properties of three
+stream food webs. \emph{Freshwater Biology}, 44, 413--422.
+
 \end{CSLReferences}

### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@b110a82e6c34a0498ade3712a5140fd3878765b4 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@78c1758c6fc8e8d2ce5414417989df6bd54ac5f3 🚀

@@
 
-Within the last several hundred years, human activity has rapidly
-changed Earth's atmosphere, oceans, and surface. Greenhouse gas
+Within the last several hundred years, human activity has induced rapid
+changes in Earth's atmosphere, oceans, and surface. Greenhouse gas
 emissions have caused an increase the temperature of both Earth's
-terrestial surface and its oceans, and both agricultural and urban
-development has rapidly reshaped the cover of Earth's surface. These the
-bulk of this change has occurred within the last several hundred years,
-a geological instant, potentially inducing shocks to ecosystems that
-could threated their integrity (\textbf{Scheffer?}). As a result
-understanding and predicting how ecosystems will change in the future,
-\emph{ecological forecasting}, and making making descisions based on
-these predictions mitigating the consequences of this change, on
-ecosystems has emerged as an imperative for ecology and environmental
-science {[}Dietze (2017);{]}.
+terrain and oceans, and both agricultural and urban development has
+rapidly reshaped the Earth's land cover. These the bulk of this change
+has occurred within the last several hundred years, a geological
+instant, inducing a sudden shift in conditions to Earth's climate and
+biosphere. As a result, predicting how ecosystems will change in the
+future, \emph{ecological forecasting}, and then using these forecasts to
+make decisions to mitigate the negative consequences of this change on
+ecosystems, their functioning, and the services they provide to humans
+has emerged as an imperative for ecology and environmental science
+(Dietze 2017). However, robust prediction of ecological processes is, to
+say the least, quite difficult (Beckage \emph{et al.} 2011; Petchey
+\emph{et al.} 2015). This difficultly is compounded by a few factors,
+the first being that sampling ecosystems is not easy. Ecological data is
+often biased, noisey, and sparse in both space and time. The current
+paucity of ecological data has resulted in much interest in developing
+global systems for \emph{ecosystem monitoring} (Makiola \emph{et al.}
+2020), which would systematize the collection of biodiversity data in
+manner that makes detecting and predicting change more possible than at
+the moment (Urban \emph{et al.} 2021).
 
@@
 
-However, robust forecasting of ecological processes will change in the
-future is, to say the least, quite difficult (Beckage \emph{et al.}
-2011; Petchey \emph{et al.} 2015). This difficultly is compounded by a
-few factors, the first being that sampling ecosystems is not easy.
-Ecological data is often biased, and noisey, spatially and temporally
-sparse. As a result \emph{ecosystem monitoring} (Makiola \emph{et al.}
-2020) has emerged as an imperative. Developing a system for ecological
-observation, which is able to coordinate across locations.
-(\textbf{AndyUrbanBiomonitoring?} paper).
-
-The second major challenge in forecasting ecosystems is that the
-underlying dynamics of most ecological processes are fundementally
-unknown (and unknowable) and instead must be inferred.
-
-Much of the history of quantitatively modeling ecosystems have been done
-in the language of dynamical systems, describing how the value of an
-observable state of the system, represented by a vector of numbers
-\([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time. It turns
-out to be much more effective to, rather than attempt to directly model
-\(\vec{x}(t)\) itself, to instead describe how \(\vec{x}\) changes from
-one timestep to the next, yielding models in the form of differential
-equations in continuous-time settings--\(\frac{dx}{dt} = f(x)\)-- or
-difference equations in discrete-time
-settings--\(x_t = f(x_{t-1})\)--where
+The second major challenge in ecological forecasting is that the
+underlying dynamics of most ecological processes are unknown and instead
+must be inferred from this (sparse) data. Much of the history of
+quantitatively modeling ecosystems have been done in the language of
+dynamical systems, describing how the value of an observable state of
+the system, represented by a vector of numbers
+\([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time, yielding
+models in the form of differential equations in continuous-time
+settings--\(\frac{dx}{dt} = f(x)\)-- or difference equations in
+discrete-time settings--\(x_t = f(x_{t-1})\)--where
 \(f:\mathbb{R}^n \to \mathbb{R}^n\) is an arbitrary function describing
@@
 of communities, \(f\) could be Lotka-Voltera, Holling-Type-III or
-DeAngelis-Beddington functional response). The form of this functional
-response in real systems is effectively unknown, and some forms are
-inherently more ``forecastable'' than others (Chen \emph{et al.} 2019).
+DeAngelis-Beddington functional response). The initial success of these
+forms of models can be traced back to the larger program of ontological
+reductionism, which became the default approach to modeling in the
+sciences after its early success in physics, which, by the time ecology
+was becoming a quantitative science (sometime in the 20th century,
+depending on who you ask), became the foundation for early quantitative
+models in ecology.
 
@@
 However, we run into many problems when aiming to apply this type of
-model to empirical data in ecology.
-
-The initial success of ODE models can be traced back to the larger
-program of ontological reductionism, which became the de facto apporoach
-model physical sciences after its early success in physics, which, by
-the time ecology was becoming a quantitative science (sometime in the
-20th century, depending on who you ask), became the foundation for early
-quantitative models in ecology.
-
-But ecosystems are perhaps the quintessential example of system that
-cannot be understood simply by iterative reduction of its components.
-Emergent phenomena, mechanisms at different scales, etc.
-
-Some have been explored in the ecological literature: (1) Some
-applications of dynamic models in ecology assume long-run equilibrium.
-(2) Stochasticity
-
-\begin{enumerate}
-\def\labelenumi{(\arabic{enumi})}
-\setcounter{enumi}{2}
-\tightlist
-\item
-  Ecological processes vary across more variables than the tools of
-  analytic models are suited for. As the number of variables in an
-  analytic model increases, so does the ability of the scientist to
-  decern clear relationships between them, and so does overfitting
-  potential. Curse of dimensionality--- Until the 20th century, no
-  theory of the gravitational dynamics of more than 2 bodies.
-  Understanding the gravitational dynamics of more than two planets with
-  any reliability proved difficult. Using the same models (diffeqs), how
-  could we adequately predict ecosystems?
-\end{enumerate}
+model to empirical data in ecology. Ecosystems are perhaps the
+quintessential example of system that cannot be understood by iterative
+reduction of its components into constituent parts---ecological
+phenomena are emergent are the product of different mechanisms operating
+a different spatial, temporal, and organizational scales (Levin 1992).
+Further, the form of this functional response in real systems is
+effectively unknown, and some forms are inherently more ``forecastable''
+than others (Beckage \emph{et al.} 2011; Chen \emph{et al.} 2019;
+Pennekamp \emph{et al.} 2019). Further this analytical approach to
+modeling explicitly ignores known realities: ecological dynamics not
+deterministic, many analytic models in ecology assume long-run
+equilibrium. Finally, perhaps the biggest challenge in using these
+models to describe ecological processes is ecosystems vary across more
+variables than the tools of analytic models are suited for. As the
+number of variables in an analytic model increases, so does the ability
+of the scientist to discern clear relationships between them given a
+fixed amount of data, the so-called ``curse'' of dimensionality.
 
@@
 
-The term \emph{ecological forecasting} implicitly creates an analogy
-between predicting how ecosystems will change in the future by using the
-term ``forecasting''---the most immediate analog being the success story
-of weather forecasting via numerical weather prediction (NWP).
+But these problems are not solely unique to ecology. The term
+\emph{ecological forecasting} implicitly creates an analogy with weather
+forecasting. Although it has become a trite joke to complain about the
+weather forecast being wrong, over the least 50 years the field of
+numerical weather prediction (NWP) has dramatically improved out ability
+to predict weather across the board (Bauer \emph{et al.} 2015). The
+success of NWP, and the Earth observations systems that support it (Hill
+\emph{et al.} 2004), should serve as a template for development of a
+system for monitoring Earth's biodiversity. Much like ecology, NWP is
+faced with high-dimensional systems that are governed by different
+mechanisms at different scales. The success of NWP is that, rather than,
+say, attempt to forecast the weather in Quebec by applying Navier-Stokes
+to entire province, to instead use simulation models which describe
+known mechanisms at different scales, and use the availability to
+increasing computational power to directly simulate many batches of
+dynamics which directly incorporate stochasticity and uncertainty in
+parameter estimates via random number generation.
 
-Although it is become almost hack to complain about the dang weather
-forecast being wrong, over the least 50 years the (Bauer \emph{et al.}
-2015).
+\textbf{P6}
 
-The success of NWP, and the Earth observations that support it should
-serve as a template for development of a system for monitoring Earth's
-biodiversity. Much like ecology, NWP is faced with high-dimensional
-systems that are governed by different mechanisms at different scales.
-
-NWP has worked because it incorporates information about data and
-meteorological processes collected at difference scales into models
-that. Use of computational methods in NWP.
-
-Much as one would not aim to forecast the weather in Quebec by applying
-Navier-Stokes, forecasting ecological systems must
-
-Transition to simulation as the solution: shift toward approach of
-building models that \emph{generate} data.
-
-(resolving the semantic ambuity of what differentiates ``mechanistic''
-vs ``phenomological'' models is out of scope for now).
-
-More broadly a reflection reflect ecology lagging behind the statistical
-methods used in sciences that face similar challenges (many dimensions,
-many mechanisms at different scales, each with stochasticity). Chaotic
-dynamics emerge from simple analytic models, and . Whether ecosystems
-actually exhibit chaotic behavior is a different question.
-
-\textbf{P5}
-
-But forecasting isn't the only difficult problem here.
-
-Transition to theme of optimization given unknown information. A
-forecast gives us a range of future values with uncertainty around them.
-Further a convenient property that a forecasting model's uncertainty
-goes up over time (if we assume the underlying process is Markov--this
-is a strong assumption but oft true of the models we fit to temporal
-data)
-
-In face of uncertainty, decision making is an optimization problem. We
-have some goal state for the future, and some estimate of what the state
-of the world will be given a set of actions. Frame optimization problem
+But forecasting is only half the story. Marx's most well known quote
+that ``philosophers have hitherto only interpreted the world in various
+ways; the point is to change it.'' Indeed, once we have a forecast about
+how an ecosystem will change in the future, what if this forecast
+predicts a critical ecosystem service will deteriorate? We are still
+left with the question, what do we in the time being to mitigate the
+negative consequences a forecast predicts? In this framing, mitigating
+the consequences of anthropogenic change on ecosystems becomes an
+optimization problem: given a forecast of the probability. We have some
+goal state for the future, and some estimate of what the state of the
+world will be given a set of actions. Frame optimization problem
 mathematically an introduce concept of solution-space and constraint.
-
-Indeed Marx's most well known quote that ``philosophers have hitherto
-only interpreted the world in various ways; the point is to change it.''
-and a necessary step toward establishing a just and sustainable world.
 
@@
 
-\textbf{P6 -- final intro para}
+\textbf{P7}
 
-Three major components here: 1) Ecosystem monitoring, 2) Forecasting
-using the products of that monitoring, and 3) Choosing the best possible
-mitigation strategy.
-
-This flow is outlined in the left panel of fig.~\ref{fig:thesis}
+This dissertation aims to formalize a framework for ecosystem monitoring
+and forecasting (fig.~\ref{fig:thesis}, left), and each chapter address
+some aspect of this pipeline to data from a monitoring network to
+forecasts to mitigation strategy (fig.~\ref{fig:thesis}, right).
 
@@
 temporally sparse and likely to contain many interaction
-``false-negatives'' (\textbf{Strydom2021?})
+``false-negatives'' (Strydom \emph{et al.} 2021).
 
@@
 
-\textbf{CH1 concept figure}
+\begin{figure}
+\centering
+\includegraphics{./figures/ch1.png}
+\caption{chapter one concept fig}
+\end{figure}
 
@@
 split into three categories. (1) Field data from three different
-locations acvross Colorado. All field sites have multiple plots across
-an elevational gradient.
+locations across Colorado. All field sites have multiple plots across an
+elevational gradient.
 
@@
 This also goes on to includes testing some assumptions of the model with
-empirical data fig.~\ref{fig:4}. which indicate our neutral model, if
-anything, underestimates the probability of false-negatives due to
-positive correlations in co-occurrence in two spatially replicated
-networks (Thompson \& Townsend 2000; Hadfield \emph{et al.}
+empirical data fig.~\ref{fig:posassoc}. which indicate our neutral
+model, if anything, underestimates the probability of false-negatives
+due to positive correlations in co-occurrence in two spatially
+replicated networks (Thompson \& Townsend 2000; Hadfield \emph{et al.}
 2014)---further I'm planning to add the field data from chapter one into
@@
 \begin{figure}
+\hypertarget{fig:posassoc}{%
 \centering
 \includegraphics{./figures/positiveassociations.png}
-\caption{f}
+\caption{f}\label{fig:posassoc}
+}
 \end{figure}
@@
 \centering
-\includegraphics{./figures/software.png}
+\includegraphics{./figures/ch4.png}
 \caption{todo}
@@
 
+\leavevmode\hypertarget{ref-Hill2004ArcEar}{}%
+Hill, C., DeLuca, C., Balaji, Suarez, M. \& Da Silva, A. (2004). The
+architecture of the Earth System Modeling Framework. \emph{Computing in
+Science Engineering}, 6, 18--28.
+
 \leavevmode\hypertarget{ref-Hubbell2001UniNeu}{}%
@@
 University Press, Princeton.
+
+\leavevmode\hypertarget{ref-Levin1992ProPat}{}%
+Levin, S.A. (1992). The Problem of Pattern and Scale in Ecology: The
+Robert H. MacArthur Award Lecture. \emph{Ecology}, 73, 1943--1967.
 
@@
 
+\leavevmode\hypertarget{ref-Pennekamp2019IntPre}{}%
+Pennekamp, F., Iles, A.C., Garland, J., Brennan, G., Brose, U., Gaedke,
+U., \emph{et al.} (2019). The intrinsic predictability of ecological
+time series and its potential to guide forecasting. \emph{Ecological
+Monographs}, 89, e01359.
+
 \leavevmode\hypertarget{ref-Petchey2015EcoFor}{}%
@@
 
+\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
+Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
+Desjardins-Proulx, P., \emph{et al.} (2021). \emph{A Roadmap Toward
+Predicting Species Interaction Networks (Across Space and Time)}
+(Preprint). EcoEvoRxiv.
+
 \leavevmode\hypertarget{ref-Thompson2000ResSol}{}%
@@
 
+\leavevmode\hypertarget{ref-Urban2021CodLif}{}%
+Urban, M.C., Travis, J.M.J., Zurell, D., Thompson, P.L., Synes, N.W.,
+Scarpa, A., \emph{et al.} (2021). Coding for Life: Designing a Platform
+for Projecting and Protecting Global Biodiversity. \emph{BioScience}.
+
 \end{CSLReferences}

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@cc438154ba9b06f029a0d427c6faaa9eb4a4dc47 🚀

@@
 
-But forecasting is only half the story. Marx's most well known quote
-that ``philosophers have hitherto only interpreted the world in various
-ways; the point is to change it.'' Indeed, once we have a forecast about
-how an ecosystem will change in the future, what if this forecast
-predicts a critical ecosystem service will deteriorate? We are still
-left with the question, what do we in the time being to mitigate the
-negative consequences a forecast predicts? In this framing, mitigating
-the consequences of anthropogenic change on ecosystems becomes an
-optimization problem: given a forecast of the probability. We have some
-goal state for the future, and some estimate of what the state of the
-world will be given a set of actions. Frame optimization problem
-mathematically an introduce concept of solution-space and constraint.
+But forecasting is only half the story---if indeed ``{[}ecologists{]}
+have hitherto only interpreted the world in various ways; the point is
+to change it,'' then once we have a forecast about how an ecosystem will
+change in the future, what if this forecast predicts a critical
+ecosystem service will deteriorate? We are still left with the question,
+what do we in the time being to mitigate the negative consequences a
+forecast predicts? In this framing, mitigating the consequences of
+anthropogenic change on ecosystems becomes an optimization problem:
+given a forecast of the probability. We have some goal state for the
+future, and some estimate of what the state of the world will be given a
+set of actions. Frame optimization problem mathematically an introduce
+concept of solution-space and constraint.
 
@@
 
-Plants and pollinators form interaction networks, called the
-``architecture of biodiversity'' (\textbf{Jordano2007?}).
+Interactions between plants and pollinators form networks of
+interactions, which structure the ``architecture of biodiversity''
+(\textbf{Jordano2007?}). The persistence, functioning, and stability of
+ecosystems emerge from these interactions, but antropogenic change
+threatens to unravel and ``rewire'' these networks
+(\textbf{CaraDonna2017IntRew?}). Plant-pollinator networks face two
+possible forms of rewiring in response to anthropogenic environmental
+change: spatial and temporal.\\
+Spatially, range shifts could cause interacting species to no longer
+overlap in space, and shifts in phenology could cause interacting
+species to no longer overlap in time.
 
-The stability, function, and persistance of ecosystems relies on the
-structure of these interactions. Antropogenic change threatens to
-unravel these networks. Two aspects to this change: spatial and
-temporal. Spatially, range shifts along elevational gradient, and
-temporall, phenological shifts.
+This chapter uses several years of data on bumblebee-flower phenology
+and interactions across several field site, each consisting of several
+plots across an elevational gradient, combined with spatial records of
+species occurrence via GBIF to forecast this uncoupling.
 
-The issue is that we don't really know what interactions are like now.
-So not only do we need to predict with data that is spatially and
-temporally sparse and likely to contain many interaction
-``false-negatives'' (Strydom \emph{et al.} 2021).
-
-This chapter uses several years of data on bee-flower phenology and
-interactions, combined with spatial records of species occurrence via
-GBIF, to forecast how much overlap there will be between
-plants/pollinators in space/time.
-
-In stages, (1) take data from multiple sites to predict a spatial
-metaweb of \emph{Bombus}-flower interactions across Colorado. (2)
-Predict how these spatial distributions will change under CMIP6. and (3)
-quantify the lack of overlap between species for which there is a
-predicted
+Addresses the EBV to forecast of EBV element of the flow from data to
+mitigation in fig.~\ref{fig:thesis}.
 
@@
 
-Split the process into parts.
+The issue is that we don't really know what interactions are like now.
+So we also need to predict interactions as they exist \emph{in the
+present} as the data we have and temporally sparse and likely to contain
+many interaction ``false-negatives'' (Strydom \emph{et al.} 2021).
+
+In stages, (1) take data from multiple sites to predict a spatial
+metaweb of \emph{Bombus}-flower interactions across Colorado. (2)
+Predict how these spatial distributions will change under CMIP6. and (3)
+quantify the lack of overlap between species for which there is a
+predicted
+
+The process of going from data to forecast can be split into the
+following parts
 
@@
 \item
-  Building an interaction prediction model. 2) Make it spatial based on
-  distributions. 3) Forecast distributions based on CMIP6.
+  Building an interaction prediction model (or rather a set of candidate
+  models, relative abundance, phylo embedding relative abundance + phylo
+  embedding) a la Strydom \emph{et al.} (2021)
+\end{enumerate}
+
+Reconstructing latent features for each species based on simulating
+trait evolution on a phylogeny (\textbf{Strydom2021FooWeb?}).
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\item
+  Make it spatial based on distributions.
+\item
+  Forecast distributions based on CMIP6
 \end{enumerate}
@@
 \item
-  we got a tree
+  we got a tree and SDMs
 \end{enumerate}
@@
 
-There are false-negatives in interation data. Co-occurrence is not the
-same thing as interaction (\textbf{cite?}), but often is used as a
-proxy.
+This chapter uses simulation models to investigate the relationship
+between species relative abundance, sampling effort, and probability of
+accurately detecting an interaction between species, and further
+proposes a method for optimizing the spatial sampling locations to
+maximize the probability of detecting an interaction between two species
+given their distributions. This addresses the optimization of monitoring
+network part of the flow from data to mitigation in
+fig.~\ref{fig:thesis}.
 
-This chapter unravels the relationship between a given species relative
-abundance and the sampling effort needed to adequately understand this
-species distribution and interactions.
-
-There is more than one way to observe a false-negative.
+As explored in the previous chapter, there are false-negatives in
+interation data. There is more than one way to observe a false-negative
+when sampling interactions: (fig.~\ref{fig:fnrtaxonomy}). It begins with
+a conceptual framework for understanding the difference in
+false-negatives in occurrence, co-occurrence, and interactions.
+Co-occurrence is not the same thing as interaction (Blanchet \emph{et
+al.} 2020), but often is used as a proxy.
 
 \begin{figure}
+\hypertarget{fig:fnrtaxonomy}{%
 \centering
 \includegraphics{./figures/ch2.png}
-\caption{taxonomy of false negatives}
+\caption{taxonomy of false negatives}\label{fig:fnrtaxonomy}
+}
 \end{figure}
 
-It begins with a conceptual framework for understanding the difference
-in false-negatives in occurrence, co-occurrence, and interactions
-(fig.~3). We use a null model of the relative-abundance distribution
-(Hubbell 2001) to simulate realized false-negatives as a function of
-varying sampling effort.
+We use a log-normal distribution as a null model of the
+relative-abundance distribution (Hubbell 2001) to simulate realized
+false-negative rate as a function of varying sampling effort.
 
 This also goes on to includes testing some assumptions of the model with
-empirical data fig.~\ref{fig:posassoc}. which indicate our neutral
-model, if anything, underestimates the probability of false-negatives
-due to positive correlations in co-occurrence in two spatially
-replicated networks (Thompson \& Townsend 2000; Hadfield \emph{et al.}
-2014)---further I'm planning to add the field data from chapter one into
-this anlysis once complete.
+empirical data fig.~\ref{fig:posassoc}, which we analytically show that
+our neutral model, if anything, underestimates the probability of
+false-negatives due to positive correlations in co-occurrence in two
+spatially replicated networks (Thompson \& Townsend 2000; Hadfield
+\emph{et al.} 2014)---further I'm planning to add the field data from
+the previous chapter into this anlysis once available.
 
@@
 
-new addition: - simulate species distribution and efficacy of detection
-given a set of observation points where the dist from observation site
-decays. optimize set of repeated sampling locations L for a \emph{known}
-distribution D. address SDM not being the territory
-
-\hypertarget{results}{%
-\subsection{Results}\label{results}}
-
-\begin{itemize}
-\tightlist
-\item
-  nonrandom association figure sampling effort under neutral model
-\end{itemize}
+Finally this chapter proposes a simulated annealing method to optimize
+the efficacy of interactoin detection given a set of observation points
+where the dist from observation site decays. optimize set of repeated
+sampling locations L for a pair of species \emph{known} distributions
+\(D_a, D_b\).
 
@@
 
-This chapter proposes a general algorithm for optimizing corridor
-placement based on a measurement of ecosystem functioning derived from
-simulations run on a proposed landscape modification. We propose various
-landscape modifications which alter the cover of a landscape,
-represented as a raster (fig.~6, left). We then compute a new resistance
-surface based on the proposed landscape modification, and based on the
-values of resistance to dispersal between each location we simulate
-spatially-explicit metapopulation dynamics model (Hanski \& Ovaskainen
-2000; Ovaskainen \emph{et al.} 2002) to estimate a distribution of time
-until extinction for each landscape modification (fig.~6, right).
+This chapter proposes a general algorithm for choosing corridor
+placement to optimize a measurement of ecosystem functioning derived
+from simulations run on each proposed landscape modification.
+
+We propose various landscape modifications which alter the cover of a
+landscape, represented as a raster (fig.~6, left). We then compute a new
+resistance surface based on the proposed landscape modification, and
+based on the values of resistance to dispersal between each location we
+simulate spatially-explicit metapopulation dynamics model (Hanski \&
+Ovaskainen 2000; Ovaskainen \emph{et al.} 2002) to estimate a
+distribution of time until extinction for each landscape modification
+(fig.~6, right).
 
@@
 \begin{itemize}
-\tightlist
 \item
   land cover -\textgreater{} resistance -\textgreater{} extinction time
-  simulated annealing to
+\item
+  brief overview of simulated annealing
+\item
+  describe how you build the proposal function
 \item
@@
 
-\hypertarget{ch4-a-software-note-on-the-resulting-packages.}{%
-\section{CH4 a software note on the resulting
-packages.}\label{ch4-a-software-note-on-the-resulting-packages.}}
+\hypertarget{chapter-four-metacommunitydynamics.jl-a-virtual-laboratory-for-community-ecology}{%
+\section{Chapter Four: MetacommunityDynamics.jl: a virtual laboratory
+for community
+ecology}\label{chapter-four-metacommunitydynamics.jl-a-virtual-laboratory-for-community-ecology}}
 
-(MetacommunityDynamics.jl: a virtual laboratory for community ecology):
-a collection of modules in the Julia language for different aspects of
-metacommunity ecology, including most of the code used for the preceding
-chapters.
+This chapter consists of a collection of modules in the Julia language
+for different aspects of community ecology, including most of the code
+used for the preceding chapters.
+
+Indeed \texttt{MetacommunityDynamics.jl} is the center of this, but due
+to the nature of the Julia language, it is interoperable with serveral
+existing packages.
+
+\texttt{EcoJulia} organization, including several which I have
+contributed to enable interoperability with MCD.jl.
+
+A diagram showing the relation between these packages is shown in
+fig.~\ref{fig:software}.
 
 \begin{figure}
+\hypertarget{fig:software}{%
 \centering
 \includegraphics{./figures/ch4.png}
-\caption{todo}
+\caption{todo}\label{fig:software}
+}
 \end{figure}
@@
 prediction in ecological systems. \emph{Ecosphere}, 2, art125.
+
+\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
+Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
+evidence of ecological interactions. \emph{Ecology Letters}, 23,
+1050--1063.
 

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@f70eeaff425c8fea2fde89c44e86ab3146ebb47f 🚀

@@
 interactions, which structure the ``architecture of biodiversity''
-(\textbf{Jordano2007?}). The persistence, functioning, and stability of
-ecosystems emerge from these interactions, but antropogenic change
-threatens to unravel and ``rewire'' these networks
-(\textbf{CaraDonna2017IntRew?}). Plant-pollinator networks face two
-possible forms of rewiring in response to anthropogenic environmental
-change: spatial and temporal.\\
+(\textbf{Jordano2007?}). The functioning and stability of ecosystems
+emerge from these interactions, but antropogenic change threatens to
+unravel and ``rewire'' these networks (\textbf{CaraDonna2017IntRew?}),
+threating the persistence of these systems. Plant-pollinator networks
+face two possible forms of rewiring in response to anthropogenic
+environmental change: spatial and temporal.\\
 Spatially, range shifts could cause interacting species to no longer
@@
 This chapter uses several years of data on bumblebee-flower phenology
-and interactions across several field site, each consisting of several
+and interactions across several field sites, each consisting of several
 plots across an elevational gradient, combined with spatial records of
-species occurrence via GBIF to forecast this uncoupling.
-
-Addresses the EBV to forecast of EBV element of the flow from data to
-mitigation in fig.~\ref{fig:thesis}.
+species occurrence via GBIF to forecast this uncoupling. This addresses
+the EBV to forecast of EBV element of the flow from data to mitigation
+in fig.~\ref{fig:thesis} (left).
 
@@
 The data for this chapter is derived from multiple souces and can be
-split into three categories. (1) Field data from three different
-locations across Colorado. All field sites have multiple plots across an
-elevational gradient.
-
-System description: lots of data on \emph{Bombus} (bumblebees) and
-wildflowers. Three different sites, (7/7/3) years each, each covering an
-elevational gradient.
+split into four categories. (1) Field data from three different field
+sites across Colorado, each with multiple plots across an elevational
+gradient, for seven, seven, and three years resptively. This data was
+collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
+Biological Laboratory) and Julian Resasco (CU Boulder). (2) GBIF spatial
+occurrence records of each of these species across Colorado, including a
+metaweb of interactions across all of Colroado taken from GBIF. (3)
+Remotely sensed data consisting of current and forecasting bioclimatic
+variables from CHELSA. (4) Phylogeny derived from NCBI GenBank barcodes
+for mitochondrial COI (bumblebees) and chloroplast rbcL (flowers).
 
@@
 
-The issue is that we don't really know what interactions are like now.
-So we also need to predict interactions as they exist \emph{in the
-present} as the data we have and temporally sparse and likely to contain
-many interaction ``false-negatives'' (Strydom \emph{et al.} 2021).
+As the data we have is spatially sparse and likely to contain many
+interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we beign
+by predicting a metaweb of interactions as they exist \emph{in the
+present}.
 
@@
 
-We propose various landscape modifications which alter the cover of a
-landscape, represented as a raster (fig.~6, left). We then compute a new
-resistance surface based on the proposed landscape modification, and
-based on the values of resistance to dispersal between each location we
-simulate spatially-explicit metapopulation dynamics model (Hanski \&
-Ovaskainen 2000; Ovaskainen \emph{et al.} 2002) to estimate a
-distribution of time until extinction for each landscape modification
-(fig.~6, right).
+\begin{figure}
+\hypertarget{fig:ch3}{%
+\centering
+\includegraphics{./figures/ch3.png}
+\caption{fig}\label{fig:ch3}
+}
+\end{figure}
 
@@
 
+We propose various landscape modifications which alter the cover of a
+landscape, represented as a raster. We then compute a new resistance
+surface based on the proposed landscape modification, and based on the
+values of resistance to dispersal between each location we simulate
+spatially-explicit metapopulation dynamics model (Hanski \& Ovaskainen
+2000; Ovaskainen \emph{et al.} 2002) to estimate a distribution of time
+until extinction for each landscape modification.
+
 \begin{itemize}
-\item
-  land cover -\textgreater{} resistance -\textgreater{} extinction time
+\tightlist
 \item
@@
 for different aspects of community ecology, including most of the code
-used for the preceding chapters.
-
-Indeed \texttt{MetacommunityDynamics.jl} is the center of this, but due
-to the nature of the Julia language, it is interoperable with serveral
-existing packages.
-
-\texttt{EcoJulia} organization, including several which I have
-contributed to enable interoperability with MCD.jl.
-
-A diagram showing the relation between these packages is shown in
-fig.~\ref{fig:software}.
+used for the preceding chapters. Indeed
+\texttt{MetacommunityDynamics.jl} (MCD.jl) is the epicenter of this set
+of tools, but due to the nature of the Julia language, MCD.jl is
+interoperable with serveral existing packages within the
+\texttt{EcoJulia} organization, including several to which I have
+contributed. A diagram showing the relation between these packages is
+shown in fig.~\ref{fig:software}.
 
@@
 \includegraphics{./figures/ch4.png}
-\caption{todo}\label{fig:software}
+\caption{The structure of the software libraries used as part of
+MCD.jl}\label{fig:software}
 }

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@82b7a567b4d655f1b771a049e0c23faba83917bd 🚀

@@
 
-\textbf{P1}
-
 Within the last several hundred years, human activity has induced rapid
@@
 
-\textbf{P2}
-
 The second major challenge in ecological forecasting is that the
@@
 
-\textbf{P3}
-
 However, we run into many problems when aiming to apply this type of
@@
 
-\textbf{P4}
-
 But these problems are not solely unique to ecology. The term
@@
 
-\textbf{P6}
-
 But forecasting is only half the story---if indeed ``{[}ecologists{]}
@@
 ecosystem service will deteriorate? We are still left with the question,
-what do we in the time being to mitigate the negative consequences a
-forecast predicts? In this framing, mitigating the consequences of
-anthropogenic change on ecosystems becomes an optimization problem:
-given a forecast of the probability. We have some goal state for the
-future, and some estimate of what the state of the world will be given a
-set of actions. Frame optimization problem mathematically an introduce
-concept of solution-space and constraint.
+what do we in the time being to mitigate the potentially negative
+consequences a forecast predicts? In this framing, mitigating the
+consequences of anthropogenic change on ecosystems becomes an
+optimization problem: given a forecast of the future state of the
+system, and some ``goal'' state for the future, the problem is then to
+optimize our intervention into the system to maximize the probability
+the system approaches our ``goal'' state. This dissertation aims to this
+framework for ecosystem monitoring and forecasting
+(fig.~\ref{fig:thesis}, left), and each chapter address some aspect of
+this pipeline to data from a monitoring network to forecasts to
+mitigation strategy (fig.~\ref{fig:thesis}, right).
 
@@
 \end{figure}
-
-\textbf{P7}
-
-This dissertation aims to formalize a framework for ecosystem monitoring
-and forecasting (fig.~\ref{fig:thesis}, left), and each chapter address
-some aspect of this pipeline to data from a monitoring network to
-forecasts to mitigation strategy (fig.~\ref{fig:thesis}, right).
 
@@
 face two possible forms of rewiring in response to anthropogenic
-environmental change: spatial and temporal.\\
-Spatially, range shifts could cause interacting species to no longer
-overlap in space, and shifts in phenology could cause interacting
-species to no longer overlap in time.
+environmental change: spatial and temporal. Spatially, range shifts
+could cause interacting species to no longer overlap in space, and
+shifts in phenology could cause interacting species to no longer overlap
+in time.
 
@@
 false-negatives due to positive correlations in co-occurrence in two
-spatially replicated networks (Thompson \& Townsend 2000; Hadfield
-\emph{et al.} 2014)---further I'm planning to add the field data from
-the previous chapter into this anlysis once available.
+sets of spatially replicated samples of interaction networks (Thompson
+\& Townsend 2000; Hadfield \emph{et al.} 2014)---further I'm planning to
+add the field data from the previous chapter into this anlysis once
+available.
 
@@
 \item
-  brief overview of simulated annealing
+  brief overview of simulated annealing describe how you build the
 \item
-  describe how you build the proposal function
-\item
-  optimize landscape optimization
+  proposal function optimize landscape optimization
 \end{itemize}

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@660240bf6e3b4134bf60bcd6197afeb33838ee85 🚀

@@
 Interactions between plants and pollinators form networks of
-interactions, which structure the ``architecture of biodiversity''
+interactions, which together create the ``architecture of biodiversity''
 (\textbf{Jordano2007?}). The functioning and stability of ecosystems
-emerge from these interactions, but antropogenic change threatens to
-unravel and ``rewire'' these networks (\textbf{CaraDonna2017IntRew?}),
-threating the persistence of these systems. Plant-pollinator networks
-face two possible forms of rewiring in response to anthropogenic
-environmental change: spatial and temporal. Spatially, range shifts
-could cause interacting species to no longer overlap in space, and
-shifts in phenology could cause interacting species to no longer overlap
-in time.
-
-This chapter uses several years of data on bumblebee-flower phenology
-and interactions across several field sites, each consisting of several
-plots across an elevational gradient, combined with spatial records of
-species occurrence via GBIF to forecast this uncoupling. This addresses
-the EBV to forecast of EBV element of the flow from data to mitigation
-in fig.~\ref{fig:thesis} (left).
+emerge from these interactions, but anthropogenic change threatens to
+unravel and ``rewire'' these interaction networks
+(\textbf{CaraDonna2017IntRew?}), threatening the persistence of these
+systems. Plant-pollinator networks face two possible forms of rewiring
+in response to anthropogenic environmental change: spatial and temporal.
+Spatially, range shifts could cause interacting species to no longer
+overlap in space, and shifts in phenology could cause interacting
+species to no longer occur at the same time of year. This chapter uses
+several years of data on bumblebee-flower phenology and interactions
+across several field sites, each consisting of several plots across an
+elevational gradient, combined with spatial records of species
+occurrence via GBIF to forecast this uncoupling. This addresses the EBV
+to forecast element of the flow from data to mitigation in
+fig.~\ref{fig:thesis} (left).
 
@@
 \includegraphics{./figures/ch1.png}
-\caption{chapter one concept fig}
+\caption{Chapter One conceptual figure. Left: the sources of data and
+how they can be synthesized. Right: The flow from data to interaction
+prediction using a few different interaction prediction models.}
 \end{figure}
@@
 
-The data for this chapter is derived from multiple souces and can be
+The data for this chapter is derived from multiple sources that can be
 split into four categories. (1) Field data from three different field
 sites across Colorado, each with multiple plots across an elevational
-gradient, for seven, seven, and three years resptively. This data was
+gradient, for seven, seven, and three years respectively. This data was
 collected by Paul CaraDonna and Jane Oglevie (from the Rocky Mountain
-Biological Laboratory) and Julian Resasco (CU Boulder). (2) GBIF spatial
-occurrence records of each of these species across Colorado, including a
-metaweb of interactions across all of Colroado taken from GBIF. (3)
-Remotely sensed data consisting of current and forecasting bioclimatic
-variables from CHELSA. (4) Phylogeny derived from NCBI GenBank barcodes
-for mitochondrial COI (bumblebees) and chloroplast rbcL (flowers).
+Biological Laboratory; RMBL) and Julian Resasco (CU Boulder). (2) GBIF
+spatial occurrence records of each of these species across Colorado,
+including a metaweb of interactions across all of Colroado taken from
+GBIF. (3) Remotely sensed data consisting of current and forecasting
+bioclimatic variables from CHELSA. (4) Phylogenies for both bee and
+flower species derived from NCBI GenBank barcodes for mitochondrial COI
+(bumblebees) and chloroplast rbcL (flowers).
 
@@
 As the data we have is spatially sparse and likely to contain many
-interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we beign
-by predicting a metaweb of interactions as they exist \emph{in the
-present}.
-
-In stages, (1) take data from multiple sites to predict a spatial
-metaweb of \emph{Bombus}-flower interactions across Colorado. (2)
-Predict how these spatial distributions will change under CMIP6. and (3)
-quantify the lack of overlap between species for which there is a
-predicted
-
-The process of going from data to forecast can be split into the
-following parts
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\tightlist
-\item
-  Building an interaction prediction model (or rather a set of candidate
-  models, relative abundance, phylo embedding relative abundance + phylo
-  embedding) a la Strydom \emph{et al.} (2021)
-\end{enumerate}
-
-Reconstructing latent features for each species based on simulating
-trait evolution on a phylogeny (\textbf{Strydom2021FooWeb?}).
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\setcounter{enumi}{1}
-\item
-  Make it spatial based on distributions.
-\item
-  Forecast distributions based on CMIP6
-\end{enumerate}
+interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we begin
+by predicting a metaweb of interactions across Colorado as they exist
+\emph{in the present}. We do this using a set of candidate interaction
+prediction models: relative abundance only, phylogenetic embedding only
+(a la (\textbf{Strydom2021FooWeb?})), niche embedding only
+(\textbf{Gravel2019BriElt?}), and all pairwise combinations of those
+constituent models. After validating each model and selecting the best
+performing model, we then predict how these distributions of each of
+these species will change under the CMIP6 consensus climate forecast
+{[}@{]}, and then finally quantify the reduction in spatial between
+species for which there is a predicted interaction.
 
@@
 \end{enumerate}
+
+\hypertarget{next-steps}{%
+\subsection{Next steps}\label{next-steps}}
 
@@
 given their distributions. This addresses the optimization of monitoring
-network part of the flow from data to mitigation in
-fig.~\ref{fig:thesis}.
+network part of the flow from data to mitigation at the top of
+fig.~\ref{fig:thesis}, left.
 
 As explored in the previous chapter, there are false-negatives in
-interation data. There is more than one way to observe a false-negative
-when sampling interactions: (fig.~\ref{fig:fnrtaxonomy}). It begins with
-a conceptual framework for understanding the difference in
-false-negatives in occurrence, co-occurrence, and interactions.
+interaction data. However, there is more than one way to observe a
+false-negative when sampling interactions: (fig.~\ref{fig:fnrtaxonomy}).
+It begins with a conceptual framework for understanding the difference
+in false-negatives in occurrence, co-occurrence, and interactions.
 Co-occurrence is not the same thing as interaction (Blanchet \emph{et
@@
 \includegraphics{./figures/ch2.png}
-\caption{taxonomy of false negatives}\label{fig:fnrtaxonomy}
+\caption{A taxonomy of occurrence, co-occurrence, and interaction false
+negatives in data}\label{fig:fnrtaxonomy}
 }
@@
 We use a log-normal distribution as a null model of the
-relative-abundance distribution (Hubbell 2001) to simulate realized
-false-negative rate as a function of varying sampling effort.
+relative-abundance distribution (Hubbell 2001) and then simulate
+realized false-negative rate as a function of varying sampling effort.
 

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@9b8500c03d670ade94e32a7b6a99476b90b73e54 🚀

@@
 emerge from these interactions, but anthropogenic change threatens to
-unravel and ``rewire'' these interaction networks
-(\textbf{CaraDonna2017IntRew?}), threatening the persistence of these
-systems. Plant-pollinator networks face two possible forms of rewiring
-in response to anthropogenic environmental change: spatial and temporal.
+unravel and ``rewire'' these interaction networks (CaraDonna \emph{et
+al.} 2017), threatening the persistence of these systems.
+Plant-pollinator networks face two possible forms of rewiring in
+response to anthropogenic environmental change: spatial and temporal.
 Spatially, range shifts could cause interacting species to no longer
@@
 As the data we have is spatially sparse and likely to contain many
-interaction ``false-negatives'' (Strydom \emph{et al.} 2021), we begin
+interaction ``false-negatives'' (Strydom \emph{et al.} 2021b), we begin
 by predicting a metaweb of interactions across Colorado as they exist
@@
 prediction models: relative abundance only, phylogenetic embedding only
-(a la (\textbf{Strydom2021FooWeb?})), niche embedding only
-(\textbf{Gravel2019BriElt?}), and all pairwise combinations of those
-constituent models. After validating each model and selecting the best
-performing model, we then predict how these distributions of each of
-these species will change under the CMIP6 consensus climate forecast
-{[}@{]}, and then finally quantify the reduction in spatial between
-species for which there is a predicted interaction.
+(a la Strydom \emph{et al.} (2021a)), niche embedding only (Gravel
+\emph{et al.} 2019), and all pairwise combinations of those constituent
+models. After validating each model and selecting the best performing
+model, we then predict how these distributions of each of these species
+will change under the CMIP6 consensus climate forecast {[}@{]}, and then
+finally quantify the reduction in spatial between species for which
+there is a predicted interaction.
 
@@
 \item
-  we got a tree and SDMs
+  we got a tree and SDMs. See appendix figure.
 \end{enumerate}
-
-\hypertarget{next-steps}{%
-\subsection{Next steps}\label{next-steps}}
 
@@
 interaction data. However, there is more than one way to observe a
-false-negative when sampling interactions: (fig.~\ref{fig:fnrtaxonomy}).
+false-negative when sampling interactions (fig.~\ref{fig:fnrtaxonomy}).
 It begins with a conceptual framework for understanding the difference
@@
 Finally this chapter proposes a simulated annealing method to optimize
-the efficacy of interactoin detection given a set of observation points
+the efficacy of interaction detection given a set of observation points
 where the dist from observation site decays. optimize set of repeated
@@
 change in a landscape? This is the question this chapter seeks to
-answer. Models for proposing corridor locations have been developed, but
+answer. Models for inferring corridor locations have been developed, but
 are limited in that are not developed around promoting some element of
 ecosystem function, but instead by trying to find the path of least
-resistance given a resistance surface (Peterman 2018).
+resistance in an existing landscape from a derived resistance surface
+(Peterman 2018).
 
@@
 
+\leavevmode\hypertarget{ref-CaraDonna2017IntRew}{}%
+CaraDonna, P.J., Petry, W.K., Brennan, R.M., Cunningham, J.L.,
+Bronstein, J.L., Waser, N.M., \emph{et al.} (2017). Interaction rewiring
+and the rapid turnover of plantpollinator networks. \emph{Ecology
+Letters}, 20, 385--394.
+
 \leavevmode\hypertarget{ref-Chen2019RevCom}{}%
@@
 framework. \emph{Ecological Applications}, 27, 2048--2060.
+
+\leavevmode\hypertarget{ref-Gravel2019BriElt}{}%
+Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
+Nyman, T., \emph{et al.} (2019). Bringing Elton and Grinnell together: A
+quantitative framework to represent the biogeography of ecological
+interaction networks. \emph{Ecography}, 42, 401--415.
 
@@
 
+\leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%
+Strydom, T., Bouskila, S., Banville, F., Barros, C., Caron, D., Farrell,
+M.J., \emph{et al.} (2021a). Food web reconstruction through
+phylogenetic transfer of low-rank network representation.
+
 \leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
 Strydom, T., Catchen, M.D., Banville, F., Caron, D., Dansereau, G.,
-Desjardins-Proulx, P., \emph{et al.} (2021). \emph{A Roadmap Toward
+Desjardins-Proulx, P., \emph{et al.} (2021b). \emph{A Roadmap Toward
 Predicting Species Interaction Networks (Across Space and Time)}

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@6aa884bf0c127b4c10519179790bd9f30f30924b 🚀

@@
 
-Interactions between plants and pollinators form networks of
-interactions, which together create the ``architecture of biodiversity''
-(\textbf{Jordano2007?}). The functioning and stability of ecosystems
+Interactions between plants and pollinators create networks of
+interactions, which together form the ``architecture of biodiversity''
+(Bascompte \& Jordano 2007). The functioning and stability of ecosystems
 emerge from these interactions, but anthropogenic change threatens to
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
+Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
+The Architecture of Biodiversity. \emph{Annual Review of Ecology,
+Evolution, and Systematics}, 38, 567--593.
+
 \leavevmode\hypertarget{ref-Bauer2015QuiRev}{}%

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@2e20d4341ce2e47ec842b54e85a9477d1e795a64 🚀

@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\tightlist
-\item
-  we got a tree and SDMs. See appendix figure.
-\end{enumerate}
+We have phylogenies and species distributions models.
+
+\begin{figure}
+\centering
+\includegraphics{./figures/trees.png}
+\caption{Phylogeny for both bumblebee species (left) and flower species
+(right)}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{./figures/sample_sdm.png}
+\caption{Example SDM for \emph{Archillea millefolium}}
+\end{figure}
 
@@
 
-Promoting landscape connectivity is important to mitigate the effects of
-land-use change on Earth's biodiversity. However, the practical
-realities of conservation mean that there is a limitation on how much we
-can modify landscapes in order to do this. So what is the best place to
-put a corridor given a constraint on how much surface-area you can
-change in a landscape? This is the question this chapter seeks to
-answer. Models for inferring corridor locations have been developed, but
-are limited in that are not developed around promoting some element of
-ecosystem function, but instead by trying to find the path of least
-resistance in an existing landscape from a derived resistance surface
-(Peterman 2018).
-
-This chapter proposes a general algorithm for choosing corridor
-placement to optimize a measurement of ecosystem functioning derived
-from simulations run on each proposed landscape modification.
+As land-use change has caused many habitats to become fragmented and
+patchy, promoting landscape connectivity has become of significant
+interest to mitigate the effects of this change on Earth's biodiversity.
+However, the practical realities of conservation mean that there is a
+limitation on how much we can modify landscapes in order to do this. So
+what is the best place to put a corridor given a constraint on how much
+surface-area you can change in a landscape? This is the question this
+chapter seeks to answer. Models for inferring corridor locations have
+been developed, but are limited in that are not developed around
+promoting some element of ecosystem function, but instead by trying to
+find the path of least resistance in an existing landscape from a
+derived resistance surface (Peterman 2018). This chapter proposes a
+general algorithm for choosing corridor placement to optimize a
+measurement of ecosystem functioning derived from simulations run on
+each proposed landscape modification.
 
@@
 until extinction for each landscape modification.
+
+We then use simulated annealing to explore the search space of possible
+modifications to estimate the modification that maximizes the time-until
+extinction of simulated metapopulation dynamics under that hypothetical
+modified landscape.
 
@@
 \section{Conclusion}\label{conclusion}}
-
-\hypertarget{appendix}{%
-\section{Appendix}\label{appendix}}
-
-\begin{figure}
-\centering
-\includegraphics{./figures/trees.png}
-\caption{trees}
-\end{figure}
 

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e0808783ac9d706a03a77dd6910f4ab87ccee32b 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@d15303db9a2596862c7e41f1f2d7d05fdc67cbc2 🚀

@@
 
-We have phylogenies and species distributions models.
+Here we show the in-progress work on the prerequisites for the analysis
+outlined above: phylogenies for both plant and bee species
+(fig.~\ref{fig:phylo}) and species distribution models for all species
+(an example shown in fig.~\ref{fig:example_sdm}).
 
 \begin{figure}
+\hypertarget{fig:phylo}{%
 \centering
@@
 \caption{Phylogeny for both bumblebee species (left) and flower species
-(right)}
+(right)}\label{fig:phylo}
+}
 \end{figure}
@@
 \begin{figure}
+\hypertarget{fig:example_sdm}{%
 \centering
 \includegraphics{./figures/sample_sdm.png}
-\caption{Example SDM for \emph{Archillea millefolium}}
+\caption{Example SDM for \emph{Archillea
+millefolium}}\label{fig:example_sdm}
+}
 \end{figure}
-
-Transition to next chapter by discussing uncertainty in interaction
-prediction across space.
 
@@
 network part of the flow from data to mitigation at the top of
-fig.~\ref{fig:thesis}, left.
+fig.~\ref{fig:thesis}, left. As explored in the previous chapter, there
+are false-negatives in interaction data. However, there is more than one
+way to observe a false-negative when sampling interactions.
+fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of false-negatives in
+occurrence, co-occurrence, and interaction data.
 
-As explored in the previous chapter, there are false-negatives in
-interaction data. However, there is more than one way to observe a
-false-negative when sampling interactions (fig.~\ref{fig:fnrtaxonomy}).
-It begins with a conceptual framework for understanding the difference
-in false-negatives in occurrence, co-occurrence, and interactions.
 Co-occurrence is not the same thing as interaction (Blanchet \emph{et
@@
 
-We use a log-normal distribution as a null model of the
-relative-abundance distribution (Hubbell 2001) and then simulate
-realized false-negative rate as a function of varying sampling effort.
+The first result is using a log-normal distribution of relative
+abundance (Hubbell 2001) to compute a null expectation of the number of
+total observations of individuals of \emph{any species} by simulating
+the process of observation on food-webs generated using the niche model
+(\textbf{williamsmart?}) with connectance parameterized by the
+flexible-links model (\textbf{cite?}). An example of this relation for
+networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.
 
-This also goes on to includes testing some assumptions of the model with
-empirical data fig.~\ref{fig:posassoc}, which we analytically show that
-our neutral model, if anything, underestimates the probability of
-false-negatives due to positive correlations in co-occurrence in two
-sets of spatially replicated samples of interaction networks (Thompson
-\& Townsend 2000; Hadfield \emph{et al.} 2014)---further I'm planning to
-add the field data from the previous chapter into this anlysis once
-available.
+\begin{figure}
+\hypertarget{fig:fnr}{%
+\centering
+\includegraphics{./figures/ch2_fnr.png}
+\caption{foo}\label{fig:fnr}
+}
+\end{figure}
+
+We then go on to testing some assumptions of this neutral model with
+empirical data. Primarily that we analytically show that our neutral
+model, if anything, underestimates the probability of false-negatives if
+there are positive associations between species co-occurrence, which we
+show exist in two sets of spatially replicated samples of interaction
+networks (Thompson \& Townsend 2000; Hadfield \emph{et al.} 2014),
+fig.~\ref{fig:posassoc}---further I'm planning to add the field data
+from the previous chapter into this analysis once available.
 
@@
 \includegraphics{./figures/positiveassociations.png}
-\caption{f}\label{fig:posassoc}
+\caption{Demonstrates positive associations in
+co-occurrence}\label{fig:posassoc}
 }
@@
 Finally this chapter proposes a simulated annealing method to optimize
-the efficacy of interaction detection given a set of observation points
-where the dist from observation site decays. optimize set of repeated
-sampling locations L for a pair of species \emph{known} distributions
-\(D_a, D_b\).
+the efficacy of interaction detection given a set of observation
+locations for a pair of species \emph{known} distributions \(D_a, D_b\).
 

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@88d3f1a8d524d165e589917fe8549b8c7c979ccd 🚀

@@
 the process of observation on food-webs generated using the niche model
-(\textbf{williamsmart?}) with connectance parameterized by the
-flexible-links model (\textbf{cite?}). An example of this relation for
-networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.
+(Williams \& Martinez 2000) with connectance parameterized by the
+flexible-links model (MacDonald \emph{et al.} 2020). An example of this
+relation for networks with varying spceies richness is shown in
+fig.~\ref{fig:fnr}.
 
@@
 
+\leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%
+MacDonald, A.A.M., Banville, F. \& Poisot, T. (2020). Revisiting the
+Links-Species Scaling Relationship in Food Webs. \emph{Patterns}, 1.
+
 \leavevmode\hypertarget{ref-Makiola2020KeyQue}{}%
@@
 
+\leavevmode\hypertarget{ref-Williams2000SimRul}{}%
+Williams, R.J. \& Martinez, N.D. (2000). Simple rules yield complex food
+webs. \emph{Nature}, 404, 180--183.
+
 \end{CSLReferences}

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@18e8021a2d77b5781398c58fb94a436bfc0cd344 🚀

@@
 model, we then predict how these distributions of each of these species
-will change under the CMIP6 consensus climate forecast {[}@{]}, and then
-finally quantify the reduction in spatial between species for which
-there is a predicted interaction.
+will change under the CMIP6 consensus climate forecast (Karger \emph{et
+al.} 2017), and then finally quantify the reduction in spatial between
+species for which there is a predicted interaction.
 
@@
 
+\leavevmode\hypertarget{ref-Karger2017CliHig}{}%
+Karger, D.N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H., Soria-Auza,
+R.W., \emph{et al.} (2017). Climatologies at high resolution for the
+earth's land surface areas. \emph{Scientific Data}, 4, 170122.
+
 \leavevmode\hypertarget{ref-Levin1992ProPat}{}%

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@794d93a51a4345d2c4e99e3bb6bf91a3eb762279 🚀

@@
 elevational gradient, combined with spatial records of species
-occurrence via GBIF to forecast this uncoupling. This addresses the EBV
-to forecast element of the flow from data to mitigation in
-fig.~\ref{fig:thesis} (left).
+occurrence via GBIF to forecast the uncoupling of the plant-pollinator
+metaweb of Colorado.
 
@@
 between species relative abundance, sampling effort, and probability of
-accurately detecting an interaction between species, and further
-proposes a method for optimizing the spatial sampling locations to
-maximize the probability of detecting an interaction between two species
-given their distributions. This addresses the optimization of monitoring
-network part of the flow from data to mitigation at the top of
+observing an interaction between species, and further proposes a method
+for optimizing the spatial sampling locations to maximize the
+probability of detecting an interaction between two species given their
+distributions. This addresses the optimization of monitoring network
+part of the flow from data to mitigation at the top of
 fig.~\ref{fig:thesis}, left. As explored in the previous chapter, there
@@
 
-The first result is using a log-normal distribution of relative
-abundance (Hubbell 2001) to compute a null expectation of the number of
-total observations of individuals of \emph{any species} by simulating
-the process of observation on food-webs generated using the niche model
+The first result is to compute a null expectation of the probability of
+an interaction false-negative as a function number of total observations
+of individuals of \emph{any species}. This is done by using a log-normal
+distribution of relative abundance (Hubbell 2001) and simulating the
+process of observation on food-webs generated using the niche model
 (Williams \& Martinez 2000) with connectance parameterized by the
@@
 model, if anything, underestimates the probability of false-negatives if
-there are positive associations between species co-occurrence, which we
-show exist in two sets of spatially replicated samples of interaction
-networks (Thompson \& Townsend 2000; Hadfield \emph{et al.} 2014),
-fig.~\ref{fig:posassoc}---further I'm planning to add the field data
-from the previous chapter into this analysis once available.
+there are positive associations between species co-occurrence, and we
+show these positive associations exist in two sets of spatially
+replicated samples of interaction networks (Thompson \& Townsend 2000;
+Hadfield \emph{et al.} 2014), fig.~\ref{fig:posassoc}---further I'm
+planning to add the field data from the previous chapter into this
+analysis once available.
 
@@
 Finally this chapter proposes a simulated annealing method to optimize
-the efficacy of interaction detection given a set of observation
-locations for a pair of species \emph{known} distributions \(D_a, D_b\).
+the a set of \(n\) points in space to maximize the probability of
+detecting an interaction between two species \(a\) and \(b\) with
+\emph{known} distributions \(D_a\), \(D_b\).
 
@@
 \includegraphics{./figures/ch3.png}
-\caption{fig}\label{fig:ch3}
+\caption{foo}\label{fig:ch3}
 }
@@
 landscape, represented as a raster. We then compute a new resistance
-surface based on the proposed landscape modification, and based on the
-values of resistance to dispersal between each location we simulate
-spatially-explicit metapopulation dynamics model (Hanski \& Ovaskainen
-2000; Ovaskainen \emph{et al.} 2002) to estimate a distribution of time
-until extinction for each landscape modification.
+surface based on the proposed landscape modification using Circuitscape
+(McRae \emph{et al.} 2008), and based on the values of resistance to
+dispersal between pair of locations we simulate spatially-explicit
+metapopulation dynamics model (Hanski \& Ovaskainen 2000; Ovaskainen
+\emph{et al.} 2002) to estimate a distribution of time until extinction
+for each landscape modification. The largest challenge in implementing
+this algorithm is the space of potential modifications grows as
+\(O(nm)\) for an \(n\) by \(m\) raster. For most actual landscapes to
+which we wish to apply this method, the set of possible modifications
+becomes uncomputably large, so we use simulated annealing to explore the
+search space of possible modifications to estimate the modification that
+maximizes the time-until extinction of simulated metapopulation dynamics
+under that hypothetical modified landscape.
 
-We then use simulated annealing to explore the search space of possible
-modifications to estimate the modification that maximizes the time-until
-extinction of simulated metapopulation dynamics under that hypothetical
-modified landscape.
-
-\begin{itemize}
-\tightlist
-\item
-  brief overview of simulated annealing describe how you build the
-\item
-  proposal function optimize landscape optimization
-\end{itemize}
+The biggest challenge in implementing simulated annealing in this
+context is defining a proposal function for landscape modifications.
+This is done by computing the minimum-spanning-tree (MST) of the spatial
+nodes, and then proposing corridors that connect nodes that are already
+connected in the MST.
 
@@
 
-This chapter consists of a collection of modules in the Julia language
-for different aspects of community ecology, including most of the code
-used for the preceding chapters. Indeed
+The final chapter consists of a collection of modules in the Julia
+language for different aspects of community ecology, including most of
+the code used for the preceding chapters. Indeed
 \texttt{MetacommunityDynamics.jl} (MCD.jl) is the epicenter of this set
@@
 
+\leavevmode\hypertarget{ref-McRae2008UsiCir}{}%
+McRae, B.H., Dickson, B.G., Keitt, T.H. \& Shah, V.B. (2008). Using
+Circuit Theory to Model Connectivity in Ecology, Evolution, and
+Conservation. \emph{Ecology}, 89, 2712--2724.
+
 \leavevmode\hypertarget{ref-Ovaskainen2002MetMod}{}%

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@fb46df1d360ffce6ec710ba72cc4c221df2f0b2a 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@22d0e6df93e011819886625b42d04f90849bf725 🚀

@@
 models in the form of differential equations in continuous-time
-settings--\(\frac{dx}{dt} = f(x)\)-- or difference equations in
-discrete-time settings--\(x_t = f(x_{t-1})\)--where
+settings, \(\frac{dx}{dt} = f(x)\), or difference equations in
+discrete-time settings, \(x_t = f(x_{t-1})\), where
 \(f:\mathbb{R}^n \to \mathbb{R}^n\) is an arbitrary function describing
@@
 of communities, \(f\) could be Lotka-Voltera, Holling-Type-III or
-DeAngelis-Beddington functional response). The initial success of these
-forms of models can be traced back to the larger program of ontological
-reductionism, which became the default approach to modeling in the
-sciences after its early success in physics, which, by the time ecology
-was becoming a quantitative science (sometime in the 20th century,
-depending on who you ask), became the foundation for early quantitative
-models in ecology.
+DeAngelis-Beddington functional response). The form of this functional
+response in real systems is effectively unknown, and some forms are
+inherently more ``forecastable'' than others (Beckage \emph{et al.}
+2011; Chen \emph{et al.} 2019; Pennekamp \emph{et al.} 2019). The
+initial success of these forms of models can be traced back to the
+larger program of ontological reductionism, which became the default
+approach to modeling in the sciences after its early success in physics,
+which, by the time ecology was becoming a quantitative science (sometime
+in the 20th century, depending on who you ask), became the foundation
+for mathematical models in ecology.
 
 However, we run into many problems when aiming to apply this type of
-model to empirical data in ecology. Ecosystems are perhaps the
+model to empirical ecological data. Ecosystems are perhaps the
 quintessential example of system that cannot be understood by iterative
 reduction of its components into constituent parts---ecological
-phenomena are emergent are the product of different mechanisms operating
-a different spatial, temporal, and organizational scales (Levin 1992).
-Further, the form of this functional response in real systems is
-effectively unknown, and some forms are inherently more ``forecastable''
-than others (Beckage \emph{et al.} 2011; Chen \emph{et al.} 2019;
-Pennekamp \emph{et al.} 2019). Further this analytical approach to
-modeling explicitly ignores known realities: ecological dynamics not
-deterministic, many analytic models in ecology assume long-run
-equilibrium. Finally, perhaps the biggest challenge in using these
-models to describe ecological processes is ecosystems vary across more
-variables than the tools of analytic models are suited for. As the
-number of variables in an analytic model increases, so does the ability
-of the scientist to discern clear relationships between them given a
-fixed amount of data, the so-called ``curse'' of dimensionality.
+phenomena are emergent: the product of different mechanisms operating a
+different spatial, temporal, and organizational scales (Levin 1992).
+Further this analytical approach to modeling explicitly ignores known
+realities: ecological dynamics not deterministic and many analytic
+models in ecology assume long-run equilibrium. Finally, perhaps the
+biggest challenge in using these models to describe ecological processes
+is ecosystems consist of more dimensions than the tools of analytic
+models are suited for. As the number of variables in an analytic model
+increases, so does the ability of the scientist to discern clear
+relationships between them given a fixed amount of data, the so-called
+``curse'' of dimensionality.
 
@@
 
-\hypertarget{methods-1}{%
-\subsection{Methods}\label{methods-1}}
-
 We propose various landscape modifications which alter the cover of a

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@1e9ee1acde888d3196c7d683b515b6fcb26423cc 🚀

@@
 
-Interactions between plants and pollinators create networks of
-interactions, which together form the ``architecture of biodiversity''
-(Bascompte \& Jordano 2007). The functioning and stability of ecosystems
-emerge from these interactions, but anthropogenic change threatens to
-unravel and ``rewire'' these interaction networks (CaraDonna \emph{et
-al.} 2017), threatening the persistence of these systems.
-Plant-pollinator networks face two possible forms of rewiring in
-response to anthropogenic environmental change: spatial and temporal.
-Spatially, range shifts could cause interacting species to no longer
-overlap in space, and shifts in phenology could cause interacting
-species to no longer occur at the same time of year. This chapter uses
-several years of data on bumblebee-flower phenology and interactions
-across several field sites, each consisting of several plots across an
-elevational gradient, combined with spatial records of species
-occurrence via GBIF to forecast the uncoupling of the plant-pollinator
-metaweb of Colorado.
+Interactions between plants and pollinators form networks which together
+structure the ``architecture of biodiversity'' (Bascompte \& Jordano
+2007). The functioning and stability of ecosystems emerge from these
+interactions, but anthropogenic change threatens to unravel and
+``rewire'' these interaction networks (CaraDonna \emph{et al.} 2017),
+jeopardizing the persistence of these systems. Plant-pollinator networks
+face two possible forms of rewiring in response to anthropogenic
+environmental change: spatial and temporal. Range shifts could cause
+interacting species to no longer overlap in space, and shifts in
+phenology could cause interacting species to no longer occur at the same
+time of year. This chapter uses several years of data on
+bumblebee-flower phenology and interactions across several field sites,
+each consisting of several plots across an elevational gradient,
+combined with spatial records of species occurrence via GBIF to forecast
+the uncoupling of the plant-pollinator metaweb of Colorado.
 
@@
 spatial occurrence records of each of these species across Colorado,
-including a metaweb of interactions across all of Colroado taken from
+including a metaweb of interactions across all of Colorado taken from
 GBIF. (3) Remotely sensed data consisting of current and forecasting

### 2021-11-21 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@9b02b7174adf7731fc95d2491dc7fc5b4108c618 🚀

@@
 \emph{et al.} 2019), and all pairwise combinations of those constituent
-models. After validating each model and selecting the best performing
-model, we then predict how these distributions of each of these species
-will change under the CMIP6 consensus climate forecast (Karger \emph{et
-al.} 2017), and then finally quantify the reduction in spatial between
+models. After validating and selecting the best performing model, we
+then predict how these distributions of each of these species will
+change under the CMIP6 consensus climate forecast (Karger \emph{et al.}
+2017), and then finally quantify the reduction in spatial between
 species for which there is a predicted interaction.

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@b40d93aa6c51b5048d941a37d5ef873e2adb69a2 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@765219f986f193eae84c6d52a51418c5a37818c4 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@5099287b68fe73e39b47b3d4744b3c0aadd2b4aa 🚀

@@
 instant, inducing a sudden shift in conditions to Earth's climate and
-biosphere. As a result, predicting how ecosystems will change in the
-future, \emph{ecological forecasting}, and then using these forecasts to
-make decisions to mitigate the negative consequences of this change on
-ecosystems, their functioning, and the services they provide to humans
-has emerged as an imperative for ecology and environmental science
-(Dietze 2017). However, robust prediction of ecological processes is, to
-say the least, quite difficult (Beckage \emph{et al.} 2011; Petchey
-\emph{et al.} 2015). This difficultly is compounded by a few factors,
-the first being that sampling ecosystems is not easy. Ecological data is
-often biased, noisey, and sparse in both space and time. The current
-paucity of ecological data has resulted in much interest in developing
-global systems for \emph{ecosystem monitoring} (Makiola \emph{et al.}
-2020), which would systematize the collection of biodiversity data in
-manner that makes detecting and predicting change more possible than at
-the moment (Urban \emph{et al.} 2021).
+biosphere. As a result \emph{ecological forecasting}---TK DEFINITION
+---and then using these forecasts to make decisions to mitigate the
+negative consequences of this change on ecosystems, their functioning,
+and the services they provide to humans has emerged as an imperative for
+ecology and environmental science (Dietze 2017). However, robust
+prediction of ecological processes is, to say the least, quite difficult
+(Beckage \emph{et al.} 2011; Petchey \emph{et al.} 2015). This
+difficultly is compounded by a few factors, the first being that
+sampling ecosystems is not easy. Ecological data is often biased,
+noisey, and sparse in both space and time. The current paucity of
+ecological data has resulted in much interest in developing global
+systems for \emph{ecosystem monitoring} (Makiola \emph{et al.} 2020),
+which would systematize the collection of biodiversity data in manner
+that makes detecting and predicting change more possible than at the
+moment (Urban \emph{et al.} 2021).
 
-The second major challenge in ecological forecasting is that the
-underlying dynamics of most ecological processes are unknown and instead
-must be inferred from this (sparse) data. Much of the history of
-quantitatively modeling ecosystems have been done in the language of
-dynamical systems, describing how the value of an observable state of
-the system, represented by a vector of numbers
+\textbf{\emph{TK add mention of interaction prediction here as they
+effect dynamics}} The second major challenge in ecological forecasting
+is that the underlying dynamics of most ecological processes are unknown
+and instead must be inferred from this (sparse) data. Much of the
+history of quantitatively modeling ecosystems have been done in the
+language of dynamical systems, describing how the value of an observable
+state of the system, represented by a vector of numbers
 \([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time, yielding
@@
 
-\hypertarget{chapter-one-forecasting-the-spatial-uncoupling-of-a-plant-pollinator-network}{%
-\section{Chapter One: Forecasting the spatial uncoupling of a
+\textbf{TK final paragraph} \textgreater{} Set up the key research
+challenges in this field so that the reader understands where your
+thesis fits in. \textgreater{} Finish the introduction with a short
+summary of what you will do across your chapters. This is the bridging
+paragraph to your chapters.
+
+The primary reserach challenges this thesis addresses: how do we design
+ecological samples? Data assimilation pipeline. How do we propgate
+uncertainty from these samples into forecasts? More details on pipeline
+flow
+
+\hypertarget{chapter-one-optimizing-spatial-sampling-of-species-interactions}{%
+\section{Chapter One: Optimizing spatial sampling of species
+interactions}\label{chapter-one-optimizing-spatial-sampling-of-species-interactions}}
+
+\hypertarget{objective}{%
+\subsection{Objective}\label{objective}}
+
+This chapter uses simulation models to investigate the relationship
+between species relative abundance, sampling effort, and probability of
+observing an interaction between species in order to aid in the design
+of samples of ecological interactions, and to provide a null expectation
+of false-negative probability for a dataset of a given size. Further it
+then proposes a method for optimizing the spatial sampling locations to
+maximize the probability of detecting an interaction between two species
+given a fixed number of total of observations, and the distributions of
+each species. This addresses the optimization of monitoring network part
+of the flow from data to mitigation at the top of fig.~\ref{fig:thesis},
+left. As explored in the previous chapter, there are false-negatives in
+interaction data. However, there is more than one way to observe a
+false-negative when sampling interactions. fig.~\ref{fig:fnrtaxonomy}
+shows a taxonomy of false-negatives in occurrence, co-occurrence, and
+interaction data.
+
+\begin{figure}
+\hypertarget{fig:fnrtaxonomy}{%
+\centering
+\includegraphics{./figures/ch2.png}
+\caption{A taxonomy of occurrence, co-occurrence, and interaction false
+negatives in data}\label{fig:fnrtaxonomy}
+}
+\end{figure}
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
+
+The first result is to compute a null expectation of the probability of
+an interaction false-negative as a function number of total observations
+of individuals of \emph{any species}. This is done by simulating the
+process of observation, where the probability of observing a given
+species is its relative abundance. We use a log-normal distribution of
+relative abundance (Hubbell 2001) and simulating the process of
+observation on food-webs generated using the niche model (Williams \&
+Martinez 2000) with connectance parameterized by the flexible-links
+model (MacDonald \emph{et al.} 2020).
+
+An example of this relation for networks with varying spceies richness
+is shown in fig.~\ref{fig:fnr}.
+
+We then go on to testing some assumptions of this neutral model with
+empirical data. Primarily that we analytically show that our neutral
+model, if anything, underestimates the probability of false-negatives if
+there are positive associations between species co-occurrence, and we
+show these positive associations exist in two sets of spatially
+replicated samples of interaction networks (Thompson \& Townsend 2000;
+Hadfield \emph{et al.} 2014), fig.~\ref{fig:posassoc}---further I'm
+planning to add the field data from the previous chapter into this
+analysis once available.
+
+\hypertarget{results}{%
+\subsection{Results}\label{results}}
+
+\begin{figure}
+\hypertarget{fig:fnr}{%
+\centering
+\includegraphics{./figures/ch2_fnr.png}
+\caption{foo}\label{fig:fnr}
+}
+\end{figure}
+
+\begin{figure}
+\hypertarget{fig:posassoc}{%
+\centering
+\includegraphics{./figures/positiveassociations.png}
+\caption{Demonstrates positive associations in
+co-occurrence}\label{fig:posassoc}
+}
+\end{figure}
+
+\hypertarget{discussion}{%
+\subsection{Discussion}\label{discussion}}
+
+Finally this chapter proposes a simulated annealing method to optimize
+the a set of \(n\) points in space to maximize the probability of
+detecting an interaction between two species \(a\) and \(b\) with
+\emph{known} distributions \(D_a\), \(D_b\).
+
+\hypertarget{progress}{%
+\subsection{Progress}\label{progress}}
+
+This chapter is mostly complete. The only remaining work is the
+implementation of simulated annealing optimization process.
+
+\hypertarget{chapter-two-forecasting-the-spatial-uncoupling-of-a-plant-pollinator-network}{%
+\section{Chapter Two: Forecasting the spatial uncoupling of a
 plant-pollinator
-network}\label{chapter-one-forecasting-the-spatial-uncoupling-of-a-plant-pollinator-network}}
+network}\label{chapter-two-forecasting-the-spatial-uncoupling-of-a-plant-pollinator-network}}
 
@@
 
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
+\hypertarget{methods-1}{%
+\subsection{Methods}\label{methods-1}}
 
@@
 
-\hypertarget{methods}{%
-\subsection{Methods}\label{methods}}
-
 As the data we have is spatially sparse and likely to contain many
@@
 
-\hypertarget{preliminary-results}{%
-\subsection{Preliminary Results}\label{preliminary-results}}
+\hypertarget{results-1}{%
+\subsection{Results}\label{results-1}}
 
@@
 
-\hypertarget{chapter-two-optimizing-spatial-sampling-of-species-interactions}{%
-\section{Chapter Two: Optimizing spatial sampling of species
-interactions}\label{chapter-two-optimizing-spatial-sampling-of-species-interactions}}
+\hypertarget{progress-1}{%
+\subsection{Progress}\label{progress-1}}
 
-This chapter uses simulation models to investigate the relationship
-between species relative abundance, sampling effort, and probability of
-observing an interaction between species, and further proposes a method
-for optimizing the spatial sampling locations to maximize the
-probability of detecting an interaction between two species given their
-distributions. This addresses the optimization of monitoring network
-part of the flow from data to mitigation at the top of
-fig.~\ref{fig:thesis}, left. As explored in the previous chapter, there
-are false-negatives in interaction data. However, there is more than one
-way to observe a false-negative when sampling interactions.
-fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of false-negatives in
-occurrence, co-occurrence, and interaction data.
-
-Co-occurrence is not the same thing as interaction (Blanchet \emph{et
-al.} 2020), but often is used as a proxy.
-
-\begin{figure}
-\hypertarget{fig:fnrtaxonomy}{%
-\centering
-\includegraphics{./figures/ch2.png}
-\caption{A taxonomy of occurrence, co-occurrence, and interaction false
-negatives in data}\label{fig:fnrtaxonomy}
-}
-\end{figure}
-
-The first result is to compute a null expectation of the probability of
-an interaction false-negative as a function number of total observations
-of individuals of \emph{any species}. This is done by using a log-normal
-distribution of relative abundance (Hubbell 2001) and simulating the
-process of observation on food-webs generated using the niche model
-(Williams \& Martinez 2000) with connectance parameterized by the
-flexible-links model (MacDonald \emph{et al.} 2020). An example of this
-relation for networks with varying spceies richness is shown in
-fig.~\ref{fig:fnr}.
-
-\begin{figure}
-\hypertarget{fig:fnr}{%
-\centering
-\includegraphics{./figures/ch2_fnr.png}
-\caption{foo}\label{fig:fnr}
-}
-\end{figure}
-
-We then go on to testing some assumptions of this neutral model with
-empirical data. Primarily that we analytically show that our neutral
-model, if anything, underestimates the probability of false-negatives if
-there are positive associations between species co-occurrence, and we
-show these positive associations exist in two sets of spatially
-replicated samples of interaction networks (Thompson \& Townsend 2000;
-Hadfield \emph{et al.} 2014), fig.~\ref{fig:posassoc}---further I'm
-planning to add the field data from the previous chapter into this
-analysis once available.
-
-\begin{figure}
-\hypertarget{fig:posassoc}{%
-\centering
-\includegraphics{./figures/positiveassociations.png}
-\caption{Demonstrates positive associations in
-co-occurrence}\label{fig:posassoc}
-}
-\end{figure}
-
-Finally this chapter proposes a simulated annealing method to optimize
-the a set of \(n\) points in space to maximize the probability of
-detecting an interaction between two species \(a\) and \(b\) with
-\emph{known} distributions \(D_a\), \(D_b\).
+I have a phylogeny and SDMs for all the species. Waiting on data
+agreement with RMBL.
 
@@
 this algorithm is the space of potential modifications grows as
-\(O(nm)\) for an \(n\) by \(m\) raster. For most actual landscapes to
+\(O((nm)!)\) for an \(n\) by \(m\) raster. For most actual landscapes to
 which we wish to apply this method, the set of possible modifications
@@
 
+\hypertarget{objective-1}{%
+\subsection{Objective}\label{objective-1}}
+
 The final chapter consists of a collection of modules in the Julia
@@
 
+We need tools to generate synthetic data from a \emph{known} set of
+mechanisms and parameters to test our methods for parameter inference
+and forecasting on this \emph{known} system to assess the effectiveness
+of these inference and forecasting methods.
+
+\hypertarget{methods-2}{%
+\subsection{Methods}\label{methods-2}}
+
+Software is structured based on DG.jl (\textbf{cite?}) and Dispersal.jl
+(\textbf{cite?}).
+
+Uses methods from EN.jl to generate metawebs, or can use empirical
+networks from Mangal.jl (\textbf{cite?}).
+
+Framework based on (\textbf{Velland2010ConSyn?}), processes divided into
+four categories: selection, dispersal, drift, speciation.
+
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
+
+\begin{figure}
+\centering
+\includegraphics{./figures/foodwebtraj.png}
+\caption{Sample output of simulated food web dynamics from
+MetacommunityDynamics.jl}
+\end{figure}
+
+\hypertarget{progress-2}{%
+\subsection{Progress}\label{progress-2}}
+
+The software as it exists is capable of simulating the biomass dynamics
+of arbitrarily large food-webs using Lotka-Volterra, Holling Type-II, or
+Holling Type-III functional responses. It currently has methods to
+implement Guassian drift, and verious forms of dispersal via
+Dispersal.jl. Also occupancy dynamics for Levins metapopulations
+(\textbf{levins1967?}), and spatially explicit Hanski metapopulatoins
+(\textbf{hanski2001?}). This is most of what needs to exist for the
+preceding chapters.
+
+Selection on arbitrary environmental variables in progress, as well as
+traits.
+
 \begin{figure}
@@
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+\hypertarget{discussion-1}{%
+\section{Discussion}\label{discussion-1}}
+
+\begin{quote}
+Describing expected/anticipated contributions of the thesis. Very
+important for QE. This should be at least half a page.
+\end{quote}
 
@@
 prediction in ecological systems. \emph{Ecosphere}, 2, art125.
-
-\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
-Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
-evidence of ecological interactions. \emph{Ecology Letters}, 23,
-1050--1063.
 

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@ba848f26beb3af983f349ea50656cbd0b13f830e 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e0c5e91694a0aa699b3e2c6a62380c918777d40d 🚀

@@
 
-\textbf{TK final paragraph} \textgreater{} Set up the key research
-challenges in this field so that the reader understands where your
-thesis fits in. \textgreater{} Finish the introduction with a short
-summary of what you will do across your chapters. This is the bridging
-paragraph to your chapters.
-
-The primary reserach challenges this thesis addresses: how do we design
-ecological samples? Data assimilation pipeline. How do we propgate
-uncertainty from these samples into forecasts? More details on pipeline
-flow
+The primary research challenges this thesis addresses: how do we design
+ecological samples to? How do we build the software infrastructure to
+assimilate data from a variety of sources? How do we propagate
+uncertainty from data to forecasts? The flow of chapters follows the
+flow in fig.~\ref{fig:thesis} (left), from data collection via a
+monitoring network, to forecasting an essential biodiversity variable
+(EBV), to optimizing mitigation strategy based on constraints. In
+chapter one, we discuss how simulation can aid in the design of
+ecological samples and monitoring network design. In chapter two we use
+data to forecast the uncoupling of a plant-pollinator network. In
+chapter three, we apply simulation methods in landscape ecology to
+optimize corridor placement with respect maximize the
+time-until-extinction of a metapopulation. The fourth and final chapter
+is the software (\emph{MetacommunityDynamics.jl}) which enables the rest
+of the dissertation.
 
@@
 Martinez 2000) with connectance parameterized by the flexible-links
-model (MacDonald \emph{et al.} 2020).
-
-An example of this relation for networks with varying spceies richness
-is shown in fig.~\ref{fig:fnr}.
+model (MacDonald \emph{et al.} 2020). An example of this relation for
+networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.
 
@@
 
+Finally this chapter proposes a simulated annealing method to optimize
+the a set of \(n\) points in space to maximize the probability of
+detecting an interaction between two species \(a\) and \(b\) with
+\emph{known} distributions \(D_a\), \(D_b\).
+
 \hypertarget{results}{%
 \subsection{Results}\label{results}}
+
+The first major result is using the simulation of the observation
+process described above to generate expectations of interaction
+false-negative rate (FNR) as a function of total number of observations,
+with the goal being for this estimate to be used as correction for
+detection error when fitting an interaction prediction model. This
+relationship varies with the total richness of the metaweb
+fig.~\ref{fig:fnr}.
 
@@
 \end{figure}
+
+The second major result is that we analytically show that the this
+simulated observation model, by assuming that there is no correlation
+between observing two species given that they interaction, actually
+underpredicts the realized false-negative interaction rate. We then
+demonstrate that this association exists in two empirical systems
+fig.~\ref{fig:posassoc}.
 
@@
 
-\hypertarget{discussion}{%
-\subsection{Discussion}\label{discussion}}
-
-Finally this chapter proposes a simulated annealing method to optimize
-the a set of \(n\) points in space to maximize the probability of
-detecting an interaction between two species \(a\) and \(b\) with
-\emph{known} distributions \(D_a\), \(D_b\).
-
 \hypertarget{progress}{%
@@
 This chapter is mostly complete. The only remaining work is the
-implementation of simulated annealing optimization process.
+implementation of simulated annealing optimization process. This will be
+done by using a proposal function which takes a set of coordinates in
+space and proposes a new location for each point based on a
+distance-decaying kernel.
 
@@
 
-Here we show the in-progress work on the prerequisites for the analysis
-outlined above: phylogenies for both plant and bee species
+Here we show the in-progress results, which are the prerequisites for
+the analysis outlined above: phylogenies for both plant and bee species
 (fig.~\ref{fig:phylo}) and species distribution models for all species
@@
 
-I have a phylogeny and SDMs for all the species. Waiting on data
+At the moment, we have derived phylogenies and SDMs for all the species
+present in the Colorado GBIF metaweb. I've also been exploring the data
+available from Julian Resasco. The primary constraint on further
+progress is that we are waiting on the finalization of a data sharing
 agreement with RMBL.
@@
 dynamics}\label{chapter-three-optimizing-corridor-placement-against-ecological-dynamics}}
+
+\hypertarget{objective-1}{%
+\subsection{Objective}\label{objective-1}}
 
@@
 each proposed landscape modification.
+
+\hypertarget{methods-2}{%
+\subsection{Methods}\label{methods-2}}
 
@@
 
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
+
+\hypertarget{progress-2}{%
+\subsection{Progress}\label{progress-2}}
+
+The current progress is that I have an algorithm for proposing landscape
+modifications and a simple implementation of simulated annealing. The
+only gap left is implementing Circuitscape estimation of resistance
+surfaces.
+
 \hypertarget{chapter-four-metacommunitydynamics.jl-a-virtual-laboratory-for-community-ecology}{%
@@
 
-\hypertarget{objective-1}{%
-\subsection{Objective}\label{objective-1}}
+\hypertarget{objective-2}{%
+\subsection{Objective}\label{objective-2}}
 
@@
 
-\hypertarget{methods-2}{%
-\subsection{Methods}\label{methods-2}}
+\begin{figure}
+\hypertarget{fig:software}{%
+\centering
+\includegraphics{./figures/ch4.png}
+\caption{The structure of the software libraries used as part of
+MCD.jl}\label{fig:software}
+}
+\end{figure}
+
+\hypertarget{methods-3}{%
+\subsection{Methods}\label{methods-3}}
 
@@
 
-\hypertarget{results-2}{%
-\subsection{Results}\label{results-2}}
+\hypertarget{results-3}{%
+\subsection{Results}\label{results-3}}
+
+Below (fig.~\ref{fig:foodwebtraj}) is a sample output of simulated
+food-web dynamics for a metaweb of 100 species generated using the
+minimum-potential-niche model with connectance \(C=0.05\) and
+forbidden-link probability of \(0.5\). The dynamics change according to
+a Lotka-Volttera functional response, dispersal (with dispersal distance
+inverse proportional to trophic-level), linear mortality, and logistic
+growth for any species at the producer trophic-level.
 
 \begin{figure}
+\hypertarget{fig:foodwebtraj}{%
 \centering
@@
 \caption{Sample output of simulated food web dynamics from
-MetacommunityDynamics.jl}
+MetacommunityDynamics.jl}\label{fig:foodwebtraj}
+}
 \end{figure}
 
-\hypertarget{progress-2}{%
-\subsection{Progress}\label{progress-2}}
+\hypertarget{progress-3}{%
+\subsection{Progress}\label{progress-3}}
 
@@
 
-\begin{figure}
-\hypertarget{fig:software}{%
-\centering
-\includegraphics{./figures/ch4.png}
-\caption{The structure of the software libraries used as part of
-MCD.jl}\label{fig:software}
-}
-\end{figure}
-
-\hypertarget{discussion-1}{%
-\section{Discussion}\label{discussion-1}}
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
 

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@3f9993b383ac890764ce6e56e86cf0289a33738f 🚀

@@
 instant, inducing a sudden shift in conditions to Earth's climate and
-biosphere. As a result \emph{ecological forecasting}---TK DEFINITION
----and then using these forecasts to make decisions to mitigate the
-negative consequences of this change on ecosystems, their functioning,
-and the services they provide to humans has emerged as an imperative for
-ecology and environmental science (Dietze 2017). However, robust
-prediction of ecological processes is, to say the least, quite difficult
-(Beckage \emph{et al.} 2011; Petchey \emph{et al.} 2015). This
-difficultly is compounded by a few factors, the first being that
-sampling ecosystems is not easy. Ecological data is often biased,
-noisey, and sparse in both space and time. The current paucity of
-ecological data has resulted in much interest in developing global
-systems for \emph{ecosystem monitoring} (Makiola \emph{et al.} 2020),
-which would systematize the collection of biodiversity data in manner
-that makes detecting and predicting change more possible than at the
-moment (Urban \emph{et al.} 2021).
+biosphere. As a result \emph{ecological forecasting}---modeling how
+ecosystems and their services will change in the future---and then using
+these forecasts to make decisions to mitigate the negative consequences
+of this change on ecosystems, their functioning, and the services they
+provide to humans has emerged as an imperative for ecology and
+environmental science (Dietze 2017). However, robust prediction of
+ecological processes is, to say the least, quite difficult (Beckage
+\emph{et al.} 2011; Petchey \emph{et al.} 2015). This difficultly is
+compounded by a few factors, the first being that sampling ecosystems is
+not easy. Ecological data is often biased, noisey, and sparse in both
+space and time. The current paucity of ecological data has resulted in
+much interest in developing global systems for \emph{ecosystem
+monitoring} (Makiola \emph{et al.} 2020), which would systematize the
+collection of biodiversity data in manner that makes detecting and
+predicting change more possible than at the moment (Urban \emph{et al.}
+2021).
 
-\textbf{\emph{TK add mention of interaction prediction here as they
-effect dynamics}} The second major challenge in ecological forecasting
-is that the underlying dynamics of most ecological processes are unknown
-and instead must be inferred from this (sparse) data. Much of the
-history of quantitatively modeling ecosystems have been done in the
-language of dynamical systems, describing how the value of an observable
-state of the system, represented by a vector of numbers
+The second major challenge in ecological forecasting is that the
+underlying dynamics of most ecological processes are unknown and instead
+must be inferred from this (sparse) data. Much of the history of
+quantitatively modeling ecosystems have been done in the language of
+dynamical systems, describing how the value of an observable state of
+the system, represented by a vector of numbers
 \([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time, yielding
@@
 DeAngelis-Beddington functional response). The form of this functional
-response in real systems is effectively unknown, and some forms are
+response in real systems, and whether it is meaningfully non-zero for a
+given species interaction, is effectively unknown, and some forms are
 inherently more ``forecastable'' than others (Beckage \emph{et al.}
@@
 planning to add the field data from the previous chapter into this
-analysis once available.
-
-Finally this chapter proposes a simulated annealing method to optimize
-the a set of \(n\) points in space to maximize the probability of
-detecting an interaction between two species \(a\) and \(b\) with
-\emph{known} distributions \(D_a\), \(D_b\).
+analysis once available. Finally this chapter proposes a simulated
+annealing method to optimize the a set of \(n\) points in space to
+maximize the probability of detecting an interaction between two species
+\(a\) and \(b\) with \emph{known} distributions \(D_a\), \(D_b\).
 
@@
 The second major result is that we analytically show that the this
-simulated observation model, by assuming that there is no correlation
-between observing two species given that they interaction, actually
-underpredicts the realized false-negative interaction rate. We then
-demonstrate that this association exists in two empirical systems
-fig.~\ref{fig:posassoc}.
+simulated observation model, by assuming that there is no association
+between observing two species given that they interact, actually under
+predicts the realized false-negative interaction rate. We then
+demonstrate that this positive association association exists in two
+empirical systems fig.~\ref{fig:posassoc}.
 
@@
 
-At the moment, we have derived phylogenies and SDMs for all the species
-present in the Colorado GBIF metaweb. I've also been exploring the data
-available from Julian Resasco. The primary constraint on further
-progress is that we are waiting on the finalization of a data sharing
-agreement with RMBL.
+At the moment, we have derived phylogenies (fig.~\ref{fig:phylo}) and
+SDMs (fig.~\ref{fig:example_sdm}) for all the species present in the
+Colorado GBIF metaweb. I've also been exploring the data available from
+Julian Resasco. The primary constraint on further progress is that we
+are waiting on the finalization of a data sharing agreement with RMBL.
 
@@
 The biggest challenge in implementing simulated annealing in this
-context is defining a proposal function for landscape modifications.
-This is done by computing the minimum-spanning-tree (MST) of the spatial
-nodes, and then proposing corridors that connect nodes that are already
-connected in the MST.
+context is defining a proposal function for landscape modifications. At
+the moment this is done by computing the minimum-spanning-tree (MST) of
+the spatial nodes, and then proposing corridors that connect nodes that
+are already connected in the MST.
 
-\hypertarget{results-2}{%
-\subsection{Results}\label{results-2}}
+The final component of this chapter is measuring the effect of land-use
+change on the robustness of the optimized corridor.
 
@@
 
-\hypertarget{results-3}{%
-\subsection{Results}\label{results-3}}
+\hypertarget{results-2}{%
+\subsection{Results}\label{results-2}}
 
@@
 Holling Type-III functional responses. It currently has methods to
-implement Guassian drift, and verious forms of dispersal via
+implement Gaussian drift, and verious forms of dispersal via
 Dispersal.jl. Also occupancy dynamics for Levins metapopulations
@@
 (\textbf{hanski2001?}). This is most of what needs to exist for the
-preceding chapters.
-
-Selection on arbitrary environmental variables in progress, as well as
-traits.
+preceding chapters. In-progress functionality includes selection (which
+affects growth-rate) on arbitrary environmental variables in progress,
+as well as traits.
 

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@79107a123952c237f3db96b90f83940c59aee596 🚀

@@
 
-Software is structured based on DG.jl (\textbf{cite?}) and Dispersal.jl
-(\textbf{cite?}).
+\texttt{MetacommunityDynamics.jl} is built on \texttt{DynamicGrids.jl},
+a library for high-performance gridded simulations in the \texttt{Julia}
+language, and Dispersal.jl (Maino \emph{et al.} 2021), and extension of
+\texttt{DynamicGrids.jl} specifically for modeling organism dispersal.
+It also contains integrations with \texttt{EcologicalNetworks.jl}
+(Poisot \emph{et al.} 2019) to generate metawebs, or can use empirical
+networks from Mangal.jl (Banville \emph{et al.} 2021).
 
-Uses methods from EN.jl to generate metawebs, or can use empirical
-networks from Mangal.jl (\textbf{cite?}).
-
-Framework based on (\textbf{Velland2010ConSyn?}), processes divided into
-four categories: selection, dispersal, drift, speciation.
+It implements the general framework for community dynamics proposed by
+(\textbf{Velland2010ConSyn?}), where all community processes can divided
+into four categories: selection, dispersal, drift, and speciation.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Banville2021ManJl}{}%
+Banville, F., Vissault, S. \& Poisot, T. (2021). Mangal.jl and
+EcologicalNetworks.jl: Two complementary packages for analyzing
+ecological networks in Julia. \emph{Journal of Open Source Software}, 6,
+2721.
+
 \leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
@@
 
+\leavevmode\hypertarget{ref-Maino2021PreGlo}{}%
+Maino, J.L., Schouten, R. \& Umina, P. (2021). Predicting the global
+invasion of Drosophila suzukii to improve Australian biosecurity
+preparedness. \emph{Journal of Applied Ecology}, 58, 789--800.
+
 \leavevmode\hypertarget{ref-Makiola2020KeyQue}{}%
@@
 
+\leavevmode\hypertarget{ref-Poisot2019EcoJl}{}%
+Poisot, T., Bélisle, Z., Hoebeke, L., Stock, M. \& Szefer, P. (2019).
+EcologicalNetworks.jl: Analysing ecological networks of species
+interactions. \emph{Ecography}, 42, 1850--1861.
+
 \leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4600018fd816aa1cdba8869d842be49bb0922f9b 🚀

@@
 \texttt{EcoJulia} organization, including several to which I have
-contributed. A diagram showing the relation between these packages is
-shown in fig.~\ref{fig:software}.
-
-We need tools to generate synthetic data from a \emph{known} set of
-mechanisms and parameters to test our methods for parameter inference
-and forecasting on this \emph{known} system to assess the effectiveness
-of these inference and forecasting methods.
+contributed. We need a software library like this to generate synthetic
+data from a \emph{known} set of mechanisms and parameters to test our
+methods for parameter inference and forecasting on this \emph{known}
+system to assess the effectiveness of these inference and forecasting
+methods.
 
@@
 
-\texttt{MetacommunityDynamics.jl} is built on \texttt{DynamicGrids.jl},
-a library for high-performance gridded simulations in the \texttt{Julia}
-language, and Dispersal.jl (Maino \emph{et al.} 2021), and extension of
-\texttt{DynamicGrids.jl} specifically for modeling organism dispersal.
-It also contains integrations with \texttt{EcologicalNetworks.jl}
-(Poisot \emph{et al.} 2019) to generate metawebs, or can use empirical
-networks from Mangal.jl (Banville \emph{et al.} 2021).
-
-It implements the general framework for community dynamics proposed by
-(\textbf{Velland2010ConSyn?}), where all community processes can divided
-into four categories: selection, dispersal, drift, and speciation.
+A diagram showing the relation between these packages is shown in
+fig.~\ref{fig:software}. \texttt{MetacommunityDynamics.jl} is built on
+\texttt{DynamicGrids.jl}, a library for high-performance gridded
+simulations in the \texttt{Julia} language, and Dispersal.jl (Maino
+\emph{et al.} 2021), and extension of \texttt{DynamicGrids.jl}
+specifically for modeling organism dispersal. It also contains
+integrations with \texttt{EcologicalNetworks.jl} (Poisot \emph{et al.}
+2019) to generate metawebs, or can use empirical networks from Mangal.jl
+(Banville \emph{et al.} 2021). It implements the general framework for
+community dynamics proposed by (\textbf{Velland2010ConSyn?}), where all
+community processes can divided into four categories: selection,
+dispersal, drift, and speciation.
 
@@
 implement Gaussian drift, and verious forms of dispersal via
-Dispersal.jl. Also occupancy dynamics for Levins metapopulations
-(\textbf{levins1967?}), and spatially explicit Hanski metapopulatoins
-(\textbf{hanski2001?}). This is most of what needs to exist for the
-preceding chapters. In-progress functionality includes selection (which
-affects growth-rate) on arbitrary environmental variables in progress,
-as well as traits.
+Dispersal.jl. Also occupancy dynamics for Levins metapopulations (Levins
+1969), and spatially explicit Hanski-Ovaskainen metapopulations (Hanski
+\& Ovaskainen 2000; Ovaskainen \emph{et al.} 2002). This is most of what
+needs to exist for the preceding chapters. In-progress functionality
+includes selection (which affects growth-rate) on arbitrary
+environmental variables in progress, as well as traits.
 
@@
 
+\leavevmode\hypertarget{ref-Levins1969DemGen}{}%
+Levins, R. (1969). Some Demographic and Genetic Consequences of
+Environmental Heterogeneity for Biological Control. \emph{Bulletin of
+the Entomological Society of America}, 15, 237--240.
+
 \leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@41bffe33263a66da386f48c0bf4dbb2d9a7ad9dd 🚀

@@
 (Banville \emph{et al.} 2021). It implements the general framework for
-community dynamics proposed by (\textbf{Velland2010ConSyn?}), where all
-community processes can divided into four categories: selection,
-dispersal, drift, and speciation.
+community dynamics proposed by Vellend (2010), where all community
+processes can divided into four categories: selection, dispersal, drift,
+and speciation.
 
@@
 
+\leavevmode\hypertarget{ref-Vellend2010ConSyn}{}%
+Vellend, M. (2010). Conceptual Synthesis in Community Ecology. \emph{The
+Quarterly Review of Biology}, 85, 183--206.
+
 \leavevmode\hypertarget{ref-Williams2000SimRul}{}%

### 2021-11-23 appendix/makereport.sh
up

@@ -1,0 +1,25 @@
+#! /usr/bin/bash
+
+
+mkdir -p tmp
+cd tmp
+
+cp ../header.tex .
+cp ../appendix.md .
+
+cp -r ../figures .
+
+pandoc ../appendix.md \
+    -s \
+    -F \
+    ~/apps/pandoc-crossref --citeproc \
+        -H header.tex \
+        -o appendix.tex
+
+
+pdflatex appendix.tex
+
+mv appendix.pdf ..
+cd ..
+
+rm -rf tmp

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@def5eea1f0f6197f1f890eb363ef588ef88ad9c2 🚀
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4d3855c0d649e889d7d07a7efd382856d0b726a4 🚀

@@
 
+\hypertarget{objective-1}{%
+\subsection{Objective}\label{objective-1}}
+
 Interactions between plants and pollinators form networks which together
@@
 
-\begin{figure}
-\hypertarget{fig:phylo}{%
-\centering
-\includegraphics{./figures/trees.png}
-\caption{Phylogeny for both bumblebee species (left) and flower species
-(right)}\label{fig:phylo}
-}
-\end{figure}
-
-\begin{figure}
-\hypertarget{fig:example_sdm}{%
-\centering
-\includegraphics{./figures/sample_sdm.png}
-\caption{Example SDM for \emph{Archillea
-millefolium}}\label{fig:example_sdm}
-}
-\end{figure}
-
 \hypertarget{progress-1}{%
@@
 
-The biggest challenge in implementing simulated annealing in this
-context is defining a proposal function for landscape modifications. At
-the moment this is done by computing the minimum-spanning-tree (MST) of
-the spatial nodes, and then proposing corridors that connect nodes that
-are already connected in the MST.
+\textbf{TK} The biggest challenge in implementing simulated annealing in
+this context is defining a proposal function for landscape
+modifications. At the moment this is done by computing the
+minimum-spanning-tree (MST) of the spatial nodes, and then proposing
+corridors that connect nodes that are already connected in the MST.
 
-The final component of this chapter is measuring the effect of land-use
-change on the robustness of the optimized corridor.
+\textbf{TK} The goal to rank the cells in the raster by priority based
+on how many times they are converted in the distribution of ``good''
+corridors after simulated annealing has reached a pseudoequilibrium.
+Further, the final component of this chapter is measuring the effect of
+land-use change on the robustness of the optimized corridor. By
+simulating various neutral models of urban and agricultural sprawl, we
+can determine if the proposed modifications
 
@@
 
-\hypertarget{objective-2}{%
-\subsection{Objective}\label{objective-2}}
+\hypertarget{objective-3}{%
+\subsection{Objective}\label{objective-3}}
 
@@
 \end{quote}
+
+Developing a system for global biodiversity monitoring is an imperative
+to mitigate biodiversity loss and its impacts on humanity. In my thesis
+I hope to provide a template for the digital infrastructure that enables
+the pipeline from data collection, to forecast, to actionable
+information, both through software that can be used to solve these
+problems (chapters one, three, four), and vignettes of how these
+software can be applied (chapters one, two).
 

### 2021-11-23 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@136bef76216683e27eb23d74f75d01a00a22fcea 🚀

@@
 \includegraphics{./figures/thesisconcept.png}
-\caption{thesis concept}\label{fig:thesis}
+\caption{Left: a framework for ecosystem monitoring, forecasting, and
+mitigation. From the top, a set of biodiversity observatories which form
+a monitoring network. Each collect various biodiversity data products.
+From this raw data, we derive essential biodiversity variables (EBVs),
+and forecast how they change over time. Based on this forecast, we wish
+to choose the best possible mitigation strategy to maximize the chance
+the realized future outcomes of the EBV approaches the target state.
+Right: Each panel represents a chapter of the thesis, which follows the
+flow of the framework on the left.}\label{fig:thesis}
 }
@@
 
+By using the success of numerical-weather prediction and the Earth
+monitoring system that supports it as a model,
+
 \hypertarget{references}{%

### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@11853fb2c1163b5fc2860dcbc4ed015897b46ca5 🚀

@@
 maximize the probability of detecting an interaction between two species
-given a fixed number of total of observations, and the distributions of
+given a fixed number of total of observations and the distributions of
 each species. This addresses the optimization of monitoring network part
 of the flow from data to mitigation at the top of fig.~\ref{fig:thesis},
-left. As explored in the previous chapter, there are false-negatives in
-interaction data. However, there is more than one way to observe a
-false-negative when sampling interactions. fig.~\ref{fig:fnrtaxonomy}
-shows a taxonomy of false-negatives in occurrence, co-occurrence, and
-interaction data.
+left. There is more than one way to observe a false-negative when
+sampling interactions. fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of
+false-negatives in occurrence, co-occurrence, and interaction data. This
+chapter untangles the relationship between co-occurrence false-negatives
+and interaction false-negatives.
 
@@
 
-The first result is to compute a null expectation of the probability of
-an interaction false-negative as a function number of total observations
-of individuals of \emph{any species}. This is done by simulating the
-process of observation, where the probability of observing a given
-species is its relative abundance. We use a log-normal distribution of
-relative abundance (Hubbell 2001) and simulating the process of
-observation on food-webs generated using the niche model (Williams \&
-Martinez 2000) with connectance parameterized by the flexible-links
-model (MacDonald \emph{et al.} 2020). An example of this relation for
-networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.
+We begin by proposing a method to compute a null expectation of the
+probability of an interaction false-negative as a function number of
+total observations of individuals of \emph{all species in the species
+pool}. This is done by simulating the process of observation, where the
+probability of observing a given species is its relative abundance. We
+use a log-normal distribution of relative abundance (Hubbell 2001) and
+simulating the process of observation on food-webs generated using the
+niche model (Williams \& Martinez 2000) with connectance parameterized
+by the flexible-links model (MacDonald \emph{et al.} 2020). An example
+of this relation for networks with varying spceies richness is shown in
+fig.~\ref{fig:fnr}.
 
@@
 \caption{Chapter One conceptual figure. Left: the sources of data and
-how they can be synthesized. Right: The flow from data to interaction
+how they can be combined. Right: The flow from data to interaction
 prediction using a few different interaction prediction models.}
@@
 
-Here we show the in-progress results, which are the prerequisites for
-the analysis outlined above: phylogenies for both plant and bee species
-(fig.~\ref{fig:phylo}) and species distribution models for all species
-(an example shown in fig.~\ref{fig:example_sdm}).
+The in-progress results are the prerequisites for the analysis outlined
+above: phylogenies for both plant and bee species (appendix figure one)
+and species distribution models for all species (an example shown in
+appendix figure two).
 
@@
 
-At the moment, we have derived phylogenies (fig.~\ref{fig:phylo}) and
-SDMs (fig.~\ref{fig:example_sdm}) for all the species present in the
-Colorado GBIF metaweb. I've also been exploring the data available from
-Julian Resasco. The primary constraint on further progress is that we
-are waiting on the finalization of a data sharing agreement with RMBL.
+At the moment, we have derived phylogenies and SDMs for all the species
+present in the Colorado GBIF metaweb (appendix figures one and two).
+I've also been exploring the data available from Julian Resasco. The
+primary constraint on further progress is that we are waiting on the
+finalization of a data sharing agreement with RMBL.
 
@@
 \includegraphics{./figures/ch3.png}
-\caption{foo}\label{fig:ch3}
+\caption{A conceptual example of how we go from a map of landcover with
+a set of points where occurrence of a species has been recorded (top
+left), to the set of all possible landscape modifications (green box,
+where each point in the green box is a unique landscape modification,
+with three examples shown as pink, red and orange dots), to computing
+resistance surfaces based on proposed landscape modifications (center)
+and then simulate the distribution of extinction times for a
+metapopulation in this new landscape (right).}\label{fig:ch3}
 }
@@
 
-\textbf{TK} The biggest challenge in implementing simulated annealing in
-this context is defining a proposal function for landscape
-modifications. At the moment this is done by computing the
-minimum-spanning-tree (MST) of the spatial nodes, and then proposing
-corridors that connect nodes that are already connected in the MST.
+The biggest challenge in implementing simulated annealing in this
+context is defining a proposal function for landscape modifications. At
+the moment this is done by computing the minimum-spanning-tree (MST) of
+the spatial nodes, and then proposing corridors that connect nodes that
+are already connected in the MST. The primary reason for doing this is
+the cut down the size of the solution space to enable quicker
+convergence, although the final software that implements this algorithm
+will enable alternative methods of proposing modifications.
 
-\textbf{TK} The goal to rank the cells in the raster by priority based
-on how many times they are converted in the distribution of ``good''
-corridors after simulated annealing has reached a pseudoequilibrium.
-Further, the final component of this chapter is measuring the effect of
-land-use change on the robustness of the optimized corridor. By
-simulating various neutral models of urban and agricultural sprawl, we
-can determine if the proposed modifications
+The goal output of this chapter is not only to provide a set of discrete
+corridor options, but also to rank the cells in the raster by priority
+based on how many times they are converted in the distribution of
+``good'' corridors after simulated annealing has reached a
+pseudoequilibrium. Further, the final component of this chapter is
+measuring the effect of land-use change on the robustness of the
+optimized corridor by simulating various neutral models of urban and
+agricultural sprawl, and determining if the proposed modifications still
+maximize time-until-extinction when the landcover in the landscape is
+not static.
 
@@
 
-\begin{quote}
-Describing expected/anticipated contributions of the thesis. Very
-important for QE. This should be at least half a page.
-\end{quote}
-
 Developing a system for global biodiversity monitoring is an imperative
@@
 
-By using the success of numerical-weather prediction and the Earth
-monitoring system that supports it as a model,
+\textbf{TK} By using the success of numerical-weather prediction and the
+Earth monitoring system that supports it as a model,
 

### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e2a0b519d1b2c9d8359dc223295000db86aacddb 🚀

@@
 probability of observing a given species is its relative abundance. We
+show that the realized false-negative rate can be quite high, simply as
+a byproduct of the distributoin of relative abundance in communities. We
 use a log-normal distribution of relative abundance (Hubbell 2001) and
@@
 fig.~\ref{fig:fnr}.
+
+\begin{figure}
+\centering
+\includegraphics{./figures/negativebinomial.png}
+\caption{Relationship between total number of observed interactions
+negatives (x-axis) and the probability that an interaction is a
+true-negative as a function of different realized false-negative rates
+(colors), assuming each observed negative is independent---the same as
+the negative-bernoulli distribution.}
+\end{figure}
 
@@
 \includegraphics{./figures/ch2_fnr.png}
-\caption{foo}\label{fig:fnr}
+\caption{The realized false-negative-rate of interaction detection
+(y-axis) as a function of the total number of observations of all
+species in the species pool (different richnesses in different colors).
+Each point is the mean of 50 replicates, with one standard-deviation in
+the first shade, and two standard deviations in the second
+shade.}\label{fig:fnr}
 }
@@
 \includegraphics{./figures/positiveassociations.png}
-\caption{Demonstrates positive associations in
-co-occurrence}\label{fig:posassoc}
+\caption{Demonstrates positive associations in co-occurrence. Left: the
+product of the marginal probability of observing two species (A and B)
+in a sample (x-axis) agaianst the computed joint probability of
+observing these species together (y-axis). Dashed line indicates
+\(y=x\), meaning no association between the two. Each point is an
+observed interaction between two species. Right: the distribution of the
+difference between these joint and marginal probabilities. Both are
+non-zero with \(p < 10^-50\) via a t-test.}\label{fig:posassoc}
 }
@@
 
-\textbf{TK} By using the success of numerical-weather prediction and the
-Earth monitoring system that supports it as a model,
+Biodiversity science would be wise to use the success of
+numerical-weather prediction and the Earth monitoring system that
+supports it as a template. Further, we should embrace methodological
+advances in computational statistics that can enable more robust
+prediction of the dynamics of complex systems than is possible using the
+tools of analytic models---not just because they can provide more
+efficacious predictions, but also because they enable a more direct
+representation of uncertainty, which is crucial for developing
+ecological forecasting models which provide actionable information to
+stakeholders.
 

### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@043949f50c1aaf922b2452842270c69e5ba20c29 🚀

@@
 response in real systems, and whether it is meaningfully non-zero for a
-given species interaction, is effectively unknown, and some forms are
-inherently more ``forecastable'' than others (Beckage \emph{et al.}
-2011; Chen \emph{et al.} 2019; Pennekamp \emph{et al.} 2019). The
-initial success of these forms of models can be traced back to the
-larger program of ontological reductionism, which became the default
-approach to modeling in the sciences after its early success in physics,
-which, by the time ecology was becoming a quantitative science (sometime
-in the 20th century, depending on who you ask), became the foundation
-for mathematical models in ecology.
+given species interaction, is effectively unknown and must be predicted
+(\textbf{Strydom2021RoaMap?}), and some forms are inherently more
+``forecastable'' than others (Beckage \emph{et al.} 2011; Chen \emph{et
+al.} 2019; Pennekamp \emph{et al.} 2019). The initial success of these
+forms of models can be traced back to the larger program of ontological
+reductionism, which became the default approach to modeling in the
+sciences after its early success in physics, which, by the time ecology
+was becoming a quantitative science (sometime in the 20th century,
+depending on who you ask), became the foundation for mathematical models
+in ecology.
 
@@
 \caption{Sample output of simulated food web dynamics from
-MetacommunityDynamics.jl}\label{fig:foodwebtraj}
+MetacommunityDynamics.jl. Timestep (x-axis), and biomass of each species
+(y-axis).}\label{fig:foodwebtraj}
 }
@@
 ecological forecasting models which provide actionable information to
-stakeholders.
+stakeholders, and to find a way for humans to live sustainably on Earth,
+the only planet on which life has ever been known to occur.
 

### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@1c06ec9a6eaa340bb2b5980df470b89d8d95a7d8 🚀

@@
 given species interaction, is effectively unknown and must be predicted
-(\textbf{Strydom2021RoaMap?}), and some forms are inherently more
+(Strydom \emph{et al.} 2021b), and some forms are inherently more
 ``forecastable'' than others (Beckage \emph{et al.} 2011; Chen \emph{et

### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@2056db570ad5def0d6b14696f23b9cb0d263a24f 🚀

@@
 
-%
 \href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
-%
-\,\textsuperscript{1,2}
 
@@
 terrain and oceans, and both agricultural and urban development has
-rapidly reshaped the Earth's land cover. These the bulk of this change
-has occurred within the last several hundred years, a geological
-instant, inducing a sudden shift in conditions to Earth's climate and
-biosphere. As a result \emph{ecological forecasting}---modeling how
-ecosystems and their services will change in the future---and then using
-these forecasts to make decisions to mitigate the negative consequences
-of this change on ecosystems, their functioning, and the services they
+rapidly reshaped Earth's land cover. The bulk of this change has
+occurred within the last several hundred years, a geological instant,
+inducing a sudden shift in conditions to Earth's climate and biosphere.
+As a result \emph{ecological forecasting}---modeling how ecosystems and
+their services will change in the future---and then using these
+forecasts to make decisions to mitigate the negative consequences of
+this change on ecosystems, their functioning, and the services they
 provide to humans has emerged as an imperative for ecology and
@@
 monitoring} (Makiola \emph{et al.} 2020), which would systematize the
-collection of biodiversity data in manner that makes detecting and
+collection of biodiversity data in a manner that makes detecting and
 predicting change more possible than at the moment (Urban \emph{et al.}
@@
 The second major challenge in ecological forecasting is that the
-underlying dynamics of most ecological processes are unknown and instead
-must be inferred from this (sparse) data. Much of the history of
+underlying dynamics of ecological processes are unknown and instead must
+be inferred from this (sparse) data. Much of the history of
 quantitatively modeling ecosystems have been done in the language of
@@
 the system, represented by a vector of numbers
-\([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes as over time, yielding
+\([x_1, x_2, \dots, x_n]^T = \vec{x}\) changes over time, yielding
 models in the form of differential equations in continuous-time
@@
 how the system changes on a moment-to-moment basis (e.g.~in the context
-of communities, \(f\) could be Lotka-Voltera, Holling-Type-III or
+of communities, \(f\) could be Lotka-Voltera, Holling-Type-II or
 DeAngelis-Beddington functional response). The form of this functional
@@
 given species interaction, is effectively unknown and must be predicted
-(Strydom \emph{et al.} 2021b), and some forms are inherently more
-``forecastable'' than others (Beckage \emph{et al.} 2011; Chen \emph{et
-al.} 2019; Pennekamp \emph{et al.} 2019). The initial success of these
-forms of models can be traced back to the larger program of ontological
-reductionism, which became the default approach to modeling in the
-sciences after its early success in physics, which, by the time ecology
-was becoming a quantitative science (sometime in the 20th century,
-depending on who you ask), became the foundation for mathematical models
-in ecology.
+(Strydom \emph{et al.} 2021b), and some forms of these dynamics are
+inherently more ``forecastable'' than others (Beckage \emph{et al.}
+2011; Chen \emph{et al.} 2019; Pennekamp \emph{et al.} 2019). The
+initial success of these forms of models can be traced back to the
+larger program of ontological reductionism, which became the default
+approach to modeling in the sciences after its early success in physics,
+which, by the time ecology was becoming a quantitative science (sometime
+in the 20th century, depending on who you ask), became the foundation
+for mathematical models in ecology.
 
@@
 reduction of its components into constituent parts---ecological
-phenomena are emergent: the product of different mechanisms operating a
+phenomena are emergent: the product of different mechanisms operating at
 different spatial, temporal, and organizational scales (Levin 1992).
@@
 is ecosystems consist of more dimensions than the tools of analytic
-models are suited for. As the number of variables in an analytic model
-increases, so does the ability of the scientist to discern clear
-relationships between them given a fixed amount of data, the so-called
-``curse'' of dimensionality.
+models are suited for. As the number of variables in a model increases,
+so does the ability of the scientist to discern clear relationships
+between them given a fixed amount of data, the so-called ``curse'' of
+dimensionality.
 
@@
 weather forecast being wrong, over the least 50 years the field of
-numerical weather prediction (NWP) has dramatically improved out ability
+numerical weather prediction (NWP) has dramatically improved our ability
 to predict weather across the board (Bauer \emph{et al.} 2015). The
-success of NWP, and the Earth observations systems that support it (Hill
+success of NWP, and the Earth observation systems that support it (Hill
 \emph{et al.} 2004), should serve as a template for development of a
@@
 mechanisms at different scales. The success of NWP is that, rather than,
-say, attempt to forecast the weather in Quebec by applying Navier-Stokes
+say, attempt to forecast the weather in Québec by applying Navier-Stokes
 to entire province, to instead use simulation models which describe
@@
 optimize our intervention into the system to maximize the probability
-the system approaches our ``goal'' state. This dissertation aims to this
-framework for ecosystem monitoring and forecasting
+the system approaches our ``goal'' state. This dissertation aims to
+provide a framework for ecosystem monitoring and forecasting
 (fig.~\ref{fig:thesis}, left), and each chapter address some aspect of
@@
 
-The primary research challenges this thesis addresses: how do we design
-ecological samples to? How do we build the software infrastructure to
-assimilate data from a variety of sources? How do we propagate
-uncertainty from data to forecasts? The flow of chapters follows the
-flow in fig.~\ref{fig:thesis} (left), from data collection via a
-monitoring network, to forecasting an essential biodiversity variable
-(EBV), to optimizing mitigation strategy based on constraints. In
-chapter one, we discuss how simulation can aid in the design of
+The primary research challenges this thesis addresses are: how do we
+design ecological samples to? How do we build the software
+infrastructure to assimilate data from a variety of sources? And how do
+we propagate uncertainty from data to forecasts? The flow of chapters
+follows the flow in fig.~\ref{fig:thesis} (left), from data collection
+via a monitoring network, to forecasting an essential biodiversity
+variable (EBV), to optimizing mitigation strategy based on constraints.
+In chapter one, we discuss how simulation can aid in the design of
 ecological samples and monitoring network design. In chapter two we use
@@
 chapter three, we apply simulation methods in landscape ecology to
-optimize corridor placement with respect maximize the
-time-until-extinction of a metapopulation. The fourth and final chapter
-is the software (\emph{MetacommunityDynamics.jl}) which enables the rest
-of the dissertation.
+optimize corridor placement to maximize the time-until-extinction of a
+metapopulation. The fourth and final chapter is the software
+(\emph{MetacommunityDynamics.jl}) which enables the rest of the
+dissertation.
 
@@
 observing an interaction between species in order to aid in the design
-of samples of ecological interactions, and to provide a null expectation
-of false-negative probability for a dataset of a given size. Further it
-then proposes a method for optimizing the spatial sampling locations to
-maximize the probability of detecting an interaction between two species
-given a fixed number of total of observations and the distributions of
-each species. This addresses the optimization of monitoring network part
-of the flow from data to mitigation at the top of fig.~\ref{fig:thesis},
-left. There is more than one way to observe a false-negative when
-sampling interactions. fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of
-false-negatives in occurrence, co-occurrence, and interaction data. This
-chapter untangles the relationship between co-occurrence false-negatives
-and interaction false-negatives.
+of samples of ecological interactions across space, and to provide a
+null expectation of the false-negative probability for a dataset of a
+given size. Further it then proposes a method for optimizing the spatial
+sampling locations to maximize the probability of detecting an
+interaction between two species given a fixed number of total of
+observations and the distributions of each species. This addresses the
+optimization of monitoring network part of the flow from data to
+mitigation at the top of fig.~\ref{fig:thesis}, left. There is more than
+one way to observe a false-negative when sampling interactions---
+fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of false-negatives in
+occurrence, co-occurrence, and interaction data. The goal of this
+chapter is to untangle the relationship between co-occurrence
+false-negatives (and their relation to relative abundance) and
+interaction false-negatives.
 
@@
 pool}. This is done by simulating the process of observation, where the
-probability of observing a given species is its relative abundance. We
-show that the realized false-negative rate can be quite high, simply as
-a byproduct of the distributoin of relative abundance in communities. We
-use a log-normal distribution of relative abundance (Hubbell 2001) and
-simulating the process of observation on food-webs generated using the
-niche model (Williams \& Martinez 2000) with connectance parameterized
-by the flexible-links model (MacDonald \emph{et al.} 2020). An example
-of this relation for networks with varying spceies richness is shown in
-fig.~\ref{fig:fnr}.
+probability that an observation is of a given species is that species'
+relative abundance. We show that the realized false-negative rate can be
+quite high, simply as a byproduct of the distribution of relative
+abundance in communities. We use a log-normal distribution of relative
+abundance (Hubbell 2001) and simulating the process of observation on
+food-webs generated using the niche model (Williams \& Martinez 2000)
+with connectance parameterized by the flexible-links model (MacDonald
+\emph{et al.} 2020). An example of this relation for networks with
+varying species richness is shown in fig.~\ref{fig:fnr}.
 
@@
 
-We then go on to testing some assumptions of this neutral model with
-empirical data. Primarily that we analytically show that our neutral
-model, if anything, underestimates the probability of false-negatives if
-there are positive associations between species co-occurrence, and we
-show these positive associations exist in two sets of spatially
-replicated samples of interaction networks (Thompson \& Townsend 2000;
-Hadfield \emph{et al.} 2014), fig.~\ref{fig:posassoc}---further I'm
-planning to add the field data from the previous chapter into this
-analysis once available. Finally this chapter proposes a simulated
-annealing method to optimize the a set of \(n\) points in space to
-maximize the probability of detecting an interaction between two species
-\(a\) and \(b\) with \emph{known} distributions \(D_a\), \(D_b\).
+We then go on to test some assumptions of this neutral model with
+empirical data. Primarily we analytically show that our neutral model,
+if anything, underestimates the probability of false-negatives if there
+are positive associations between species co-occurrence, and we show
+these positive associations exist in two sets of spatially replicated
+samples of interaction networks (Thompson \& Townsend 2000; Hadfield
+\emph{et al.} 2014), fig.~\ref{fig:posassoc}---further I'm planning to
+add the field data from chapter two into this analysis once available.
+Finally this chapter proposes a simulated annealing method to optimize
+the a set of \(n\) points in space to maximize the probability of
+detecting an interaction between two species \(a\) and \(b\) with
+\emph{known} distributions \(D_a\), \(D_b\).
 
@@
 detection error when fitting an interaction prediction model. This
-relationship varies with the total richness of the metaweb
-fig.~\ref{fig:fnr}.
+relationship varies with the total richness of the metaweb (see
+fig.~\ref{fig:fnr}).
 
@@
 including a metaweb of interactions across all of Colorado taken from
-GBIF. (3) Remotely sensed data consisting of current and forecasting
+GBIF. (3) Remotely sensed data consisting of current and forecasted
 bioclimatic variables from CHELSA. (4) Phylogenies for both bee and
@@
 As the data we have is spatially sparse and likely to contain many
-interaction ``false-negatives'' (Strydom \emph{et al.} 2021b), we begin
-by predicting a metaweb of interactions across Colorado as they exist
-\emph{in the present}. We do this using a set of candidate interaction
-prediction models: relative abundance only, phylogenetic embedding only
-(a la Strydom \emph{et al.} (2021a)), niche embedding only (Gravel
-\emph{et al.} 2019), and all pairwise combinations of those constituent
-models. After validating and selecting the best performing model, we
-then predict how these distributions of each of these species will
-change under the CMIP6 consensus climate forecast (Karger \emph{et al.}
-2017), and then finally quantify the reduction in spatial between
-species for which there is a predicted interaction.
+interaction false-negatives, we begin by predicting a metaweb of
+interactions across Colorado as they exist \emph{in the present}. We do
+this using a set of candidate interaction prediction models: relative
+abundance only, phylogenetic embedding only (a la Strydom \emph{et al.}
+(2021a)), niche embedding only (encompassing both phenology and
+environmental niche, similar to Gravel \emph{et al.} (2019)), and all
+pairwise combinations of those constituent models. After validating and
+selecting the best performing model, we then predict how these
+distributions of each of these species will change under the CMIP6
+consensus climate forecast (Karger \emph{et al.} 2017), and then finally
+quantify the reduction in spatial overlap between species for which
+there is a predicted interaction.
 
@@
 find the path of least resistance in an existing landscape from a
-derived resistance surface (Peterman 2018). This chapter proposes a
-general algorithm for choosing corridor placement to optimize a
-measurement of ecosystem functioning derived from simulations run on
-each proposed landscape modification.
+derived resistance surface (e.g. Peterman 2018). This chapter proposes a
+general algorithm for optimizing spatial restoration effort to move a
+measurement of ecosystem functioning toward a target state.
 
@@
 
-We propose various landscape modifications which alter the cover of a
+We propose various landscape modifications that alter the cover of a
 landscape, represented as a raster. We then compute a new resistance
@@
 dispersal between pair of locations we simulate spatially-explicit
-metapopulation dynamics model (Hanski \& Ovaskainen 2000; Ovaskainen
-\emph{et al.} 2002) to estimate a distribution of time until extinction
-for each landscape modification. The largest challenge in implementing
-this algorithm is the space of potential modifications grows as
-\(O((nm)!)\) for an \(n\) by \(m\) raster. For most actual landscapes to
-which we wish to apply this method, the set of possible modifications
-becomes uncomputably large, so we use simulated annealing to explore the
-search space of possible modifications to estimate the modification that
+metapopulation dynamics (Hanski \& Ovaskainen 2000; Ovaskainen \emph{et
+al.} 2002) to estimate a distribution of time-until-extinction for each
+landscape modification. The largest challenge in implementing this
+algorithm is the space of potential modifications grows as \(O((nm)!)\)
+for an \(n\) by \(m\) raster. For most actual landscapes to which we
+wish to apply this method, the set of possible modifications becomes
+uncomputably large, so we use simulated annealing to explore the search
+space of possible modifications to estimate the modification that
 maximizes the time-until extinction of simulated metapopulation dynamics
@@
 the moment this is done by computing the minimum-spanning-tree (MST) of
-the spatial nodes, and then proposing corridors that connect nodes that
-are already connected in the MST. The primary reason for doing this is
-the cut down the size of the solution space to enable quicker
-convergence, although the final software that implements this algorithm
-will enable alternative methods of proposing modifications.
+the spatial nodes (locations where occurrence has been observed), and
+then proposing corridors that only connect nodes that are already
+connected in the MST. The primary reason for doing this is the cut down
+the size of the solution space to enable quicker convergence, although
+the final software that implements this algorithm will enable
+alternative methods of proposing modifications.
 
@@
 corridor options, but also to rank the cells in the raster by priority
-based on how many times they are converted in the distribution of
-``good'' corridors after simulated annealing has reached a
-pseudoequilibrium. Further, the final component of this chapter is
-measuring the effect of land-use change on the robustness of the
-optimized corridor by simulating various neutral models of urban and
-agricultural sprawl, and determining if the proposed modifications still
-maximize time-until-extinction when the landcover in the landscape is
-not static.
+based on how many times they are included in the distribution of
+``good'' corridors after simulated annealing has converged. Further, the
+final component of this chapter is measuring the effect of land-use
+change on the robustness of the optimized corridor by simulating various
+neutral models of urban and agricultural sprawl, and determining if the
+proposed modifications still maximize time-until-extinction when the
+landcover in the landscape is not static.
 
@@
 
-The current progress is that I have an algorithm for proposing landscape
-modifications and a simple implementation of simulated annealing. The
-only gap left is implementing Circuitscape estimation of resistance
-surfaces.
+Currently I have an algorithm for proposing landscape modifications and
+a simple implementation of simulated annealing. The only gap left is
+implementing Circuitscape estimation of resistance surfaces and running
+benchmarking tests for the resulting chapter.
 
@@
 
-The final chapter consists of a collection of modules in the Julia
-language for different aspects of community ecology, including most of
-the code used for the preceding chapters. Indeed
-\texttt{MetacommunityDynamics.jl} (MCD.jl) is the epicenter of this set
+The final chapter consists of a collection of modules in the
+\texttt{Julia} language for different aspects of community ecology,
+including most of the code used for the preceding chapters. Indeed
+\texttt{MetacommunityDynamics.jl} (MCD.jl) is at the center of this set
 of tools, but due to the nature of the Julia language, MCD.jl is
-interoperable with serveral existing packages within the
+inter-operable with several existing packages within the
 \texttt{EcoJulia} organization, including several to which I have
@@
 
-Below (fig.~\ref{fig:foodwebtraj}) is a sample output of simulated
+In fig.~\ref{fig:foodwebtraj} we see a sample output of simulated
 food-web dynamics for a metaweb of 100 species generated using the
-minimum-potential-niche model with connectance \(C=0.05\) and
-forbidden-link probability of \(0.5\). The dynamics change according to
-a Lotka-Volttera functional response, dispersal (with dispersal distance
-inverse proportional to trophic-level), linear mortality, and logistic
-growth for any species at the producer trophic-level.
+minimum-potential-niche model (Allesina \emph{et al.} 2008) with
+connectance \(C=0.05\) and forbidden-link probability of \(0.5\). The
+dynamics change according to a Lotka-Volterra functional response,
+dispersal with distance inversely proportional to trophic-level, linear
+mortality, and logistic growth for any species at the producer
+trophic-level.
 
@@
 Holling Type-III functional responses. It currently has methods to
-implement Gaussian drift, and verious forms of dispersal via
-Dispersal.jl. Also occupancy dynamics for Levins metapopulations (Levins
-1969), and spatially explicit Hanski-Ovaskainen metapopulations (Hanski
-\& Ovaskainen 2000; Ovaskainen \emph{et al.} 2002). This is most of what
-needs to exist for the preceding chapters. In-progress functionality
-includes selection (which affects growth-rate) on arbitrary
-environmental variables in progress, as well as traits.
+implement Gaussian drift, and various forms of dispersal via
+\texttt{Dispersal.jl}. Also functional are occupancy dynamics for Levins
+metapopulations (Levins 1969), and spatially explicit Hanski-Ovaskainen
+metapopulations (Hanski \& Ovaskainen 2000; Ovaskainen \emph{et al.}
+2002). This is most of what needs to exist for the preceding chapters.
+In-progress functionality includes selection (which affects growth-rate)
+on arbitrary environmental variables in progress, as well as traits.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Allesina2008GenMod}{}%
+Allesina, S., Alonso, D. \& Pascual, M. (2008). A General Model for Food
+Web Structure. \emph{Science}, 320, 658--661.
+
 \leavevmode\hypertarget{ref-Banville2021ManJl}{}%

### 2021-11-24 preprint.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@2056db570ad5def0d6b14696f23b9cb0d263a24f 🚀

@@
 {\small
-%
 \href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
-%
-\,\textsuperscript{1,2}
 \vskip 1em

### 2021-11-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@4d7e4022ce3e32b44c8b4320cbf5baf230976336 🚀

@@
 changes in Earth's atmosphere, oceans, and surface. Greenhouse gas
-emissions have caused an increase the temperature of both Earth's
+emissions have caused an increase in the temperature of both Earth's
 terrain and oceans, and both agricultural and urban development has
@@
 how the system changes on a moment-to-moment basis (e.g.~in the context
-of communities, \(f\) could be Lotka-Voltera, Holling-Type-II or
+of communities, \(f\) could be Lotka-Volterra, Holling-Type-II or
 DeAngelis-Beddington functional response). The form of this functional
@@
 forecasting. Although it has become a trite joke to complain about the
-weather forecast being wrong, over the least 50 years the field of
+weather forecast being wrong, over the last 50 years the field of
 numerical weather prediction (NWP) has dramatically improved our ability
@@
 ecosystem service will deteriorate? We are still left with the question,
-what do we in the time being to mitigate the potentially negative
+what do we do in the time being to mitigate the potentially negative
 consequences a forecast predicts? In this framing, mitigating the
@@
 provide a framework for ecosystem monitoring and forecasting
-(fig.~\ref{fig:thesis}, left), and each chapter address some aspect of
+(fig.~\ref{fig:thesis}, left), and each chapter addresses some aspect of
 this pipeline to data from a monitoring network to forecasts to
@@
 The primary research challenges this thesis addresses are: how do we
-design ecological samples to? How do we build the software
+design ecological samples to detect change? How do we build the software
 infrastructure to assimilate data from a variety of sources? And how do
@@
 null expectation of the false-negative probability for a dataset of a
-given size. Further it then proposes a method for optimizing the spatial
-sampling locations to maximize the probability of detecting an
+given size. Further, it then proposes a method for optimizing the
+spatial sampling locations to maximize the probability of detecting an
 interaction between two species given a fixed number of total of
@@
 (colors), assuming each observed negative is independent---the same as
-the negative-bernoulli distribution.}
+the negative-Bernoulli distribution.}
 \end{figure}
@@
 \includegraphics{./figures/ch1.png}
-\caption{Chapter One conceptual figure. Left: the sources of data and
+\caption{Chapter two conceptual figure. Left: the sources of data and
 how they can be combined. Right: The flow from data to interaction
@@
 then proposing corridors that only connect nodes that are already
-connected in the MST. The primary reason for doing this is the cut down
-the size of the solution space to enable quicker convergence, although
-the final software that implements this algorithm will enable
+connected in the MST. The primary reason for doing this is to the cut
+down the size of the search space to enable quicker convergence,
+although the final software that implements this algorithm will enable
 alternative methods of proposing modifications.

### 2021-11-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@ef1c555be2d8ab4689ed048597fb1e7a05131721 🚀

@@
 
+\hypertarget{context}{%
+\subsection{Context}\label{context}}
+
+Ecosystems are composed of interactions between species, yet this
+remains one of the greatest shortfalls of data in biodiversity science
+(Strydom \emph{et al.} 2021b). This is, in no small part, because
+species interactions are considerably more difficult to sample than
+single-species processes. However, understanding and predicting species
+interactions, and how anthropogenic change is affecting them, is one of
+the grand challenges faced by modern ecologists (Jordano 2016). Further,
+co-occurrence is often used as a proxy for species interaction when this
+is not necessary always a valid assumption (Blanchet \emph{et al.}
+2020).
+
 \hypertarget{objective}{%
@@
 
-This chapter uses simulation models to investigate the relationship
-between species relative abundance, sampling effort, and probability of
-observing an interaction between species in order to aid in the design
-of samples of ecological interactions across space, and to provide a
-null expectation of the false-negative probability for a dataset of a
-given size. Further, it then proposes a method for optimizing the
-spatial sampling locations to maximize the probability of detecting an
-interaction between two species given a fixed number of total of
-observations and the distributions of each species. This addresses the
-optimization of monitoring network part of the flow from data to
-mitigation at the top of fig.~\ref{fig:thesis}, left. There is more than
-one way to observe a false-negative when sampling interactions---
-fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of false-negatives in
-occurrence, co-occurrence, and interaction data. The goal of this
-chapter is to untangle the relationship between co-occurrence
-false-negatives (and their relation to relative abundance) and
-interaction false-negatives.
+The goal of this chapter is to use simulation models to investigate the
+relationship between species relative abundance, sampling effort, and
+probability of observing an interaction between species in order to aid
+in the design of samples of ecological interactions across space, and to
+provide a null expectation of the false-negative probability for a
+dataset of a given size. Further, it then proposes a method for
+optimizing the spatial sampling locations to maximize the probability of
+detecting an interaction between two species given a fixed number of
+total of observations and the distributions of each species. This
+addresses the optimization of monitoring network part of the flow from
+data to mitigation at the top of fig.~\ref{fig:thesis}, left.
 
@@
 
-\hypertarget{objective-1}{%
-\subsection{Objective}\label{objective-1}}
+\hypertarget{context-1}{%
+\subsection{Context}\label{context-1}}
 
@@
 phenology could cause interacting species to no longer occur at the same
-time of year. This chapter uses several years of data on
-bumblebee-flower phenology and interactions across several field sites,
-each consisting of several plots across an elevational gradient,
-combined with spatial records of species occurrence via GBIF to forecast
-the uncoupling of the plant-pollinator metaweb of Colorado.
+time of year.
+
+\hypertarget{objective-1}{%
+\subsection{Objective}\label{objective-1}}
+
+This chapter uses several years of data on bumblebee-flower phenology
+and interactions across several field sites, each consisting of several
+plots across an elevational gradient, combined with spatial records of
+species occurrence via GBIF to forecast the uncoupling of the
+plant-pollinator metaweb of Colorado.
 
@@
 
+\hypertarget{context-2}{%
+\subsection{Context}\label{context-2}}
+
+As land-use change has caused many habitats to become fragmented and
+patchy, promoting landscape connectivity has become of significant
+interest to mitigate the effects of this change on Earth's biodiversity
+(Resasco 2019). However, the practical realities of conservation mean
+that there is a limitation on how much we can modify landscapes in order
+to do this.
+
 \hypertarget{objective-2}{%
@@
 
-As land-use change has caused many habitats to become fragmented and
-patchy, promoting landscape connectivity has become of significant
-interest to mitigate the effects of this change on Earth's biodiversity.
-However, the practical realities of conservation mean that there is a
-limitation on how much we can modify landscapes in order to do this. So
-what is the best place to put a corridor given a constraint on how much
+What is the best place to put a corridor given a constraint on how much
 surface-area you can change in a landscape? This is the question this
@@
 general algorithm for optimizing spatial restoration effort to move a
-measurement of ecosystem functioning toward a target state.
+measurement of ecological dynamics toward a target state.
 
@@
 
+\hypertarget{context-3}{%
+\subsection{Context}\label{context-3}}
+
+Building models for ecological forecasting is an imperative (Dietze
+\emph{et al.} 2018), but before applying forecasting methods to actual
+data, we need a way to determine the efficacy of different forecasting
+methods. We need a software library like this to generate synthetic data
+from a \emph{known} set of mechanisms and parameters to test our methods
+for parameter inference and forecasting on a system with \emph{known}
+ground-truth dynamics to assess the effectiveness of these inference and
+forecasting methods.
+
 \hypertarget{objective-3}{%
@@
 \texttt{EcoJulia} organization, including several to which I have
-contributed. We need a software library like this to generate synthetic
-data from a \emph{known} set of mechanisms and parameters to test our
-methods for parameter inference and forecasting on this \emph{known}
-system to assess the effectiveness of these inference and forecasting
-methods.
+contributed.
 
@@
 
+\leavevmode\hypertarget{ref-Blanchet2020CooNot}{}%
+Blanchet, F.G., Cazelles, K. \& Gravel, D. (2020). Co-occurrence is not
+evidence of ecological interactions. \emph{Ecology Letters}, 23,
+1050--1063.
+
 \leavevmode\hypertarget{ref-CaraDonna2017IntRew}{}%
@@
 framework. \emph{Ecological Applications}, 27, 2048--2060.
+
+\leavevmode\hypertarget{ref-Dietze2018IteNea}{}%
+Dietze, M.C., Fox, A., Beck-Johnson, L.M., Betancourt, J.L., Hooten,
+M.B., Jarnevich, C.S., \emph{et al.} (2018). Iterative near-term
+ecological forecasting: Needs, opportunities, and challenges.
+\emph{Proceedings of the National Academy of Sciences}, 115, 1424--1432.
 
@@
 University Press, Princeton.
+
+\leavevmode\hypertarget{ref-Jordano2016ChaEco}{}%
+Jordano, P. (2016). Chasing Ecological Interactions. \emph{PLOS
+Biology}, 14, e1002559.
 
@@
 
+\leavevmode\hypertarget{ref-Resasco2019MetDec}{}%
+Resasco, J. (2019). Meta-analysis on a Decade of Testing Corridor
+Efficacy: What New Have we Learned? \emph{Current Landscape Ecology
+Reports}, 4, 61--69.
+
 \leavevmode\hypertarget{ref-Strydom2021FooWeb}{}%

### 2021-11-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@e3eace70cbd0949351a6bc37146e430c2115ef4b 🚀

@@
 data, we need a way to determine the efficacy of different forecasting
-methods. We need a software library like this to generate synthetic data
-from a \emph{known} set of mechanisms and parameters to test our methods
-for parameter inference and forecasting on a system with \emph{known}
+methods. We need a software library to generate synthetic data from a
+\emph{known} set of mechanisms and parameters to test our methods for
+parameter inference and forecasting on a system with \emph{known}
 ground-truth dynamics to assess the effectiveness of these inference and
